\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{longtable}
\usepackage{array}
\begin{document}
\section*{FLCR-07 - Causal Links And Obligation Ledgers}

**Series:** Formalizing LCR, Unifying Standard Models
**Artifact:** formal paper source
**Status:** first-pass rich rewrite; requires final citation and build pass.
**Claim posture:** maximal local claim posture with explicit lane boundaries.

\subsection*{Abstract}

This paper turns the FLCR corpus into an auditable dependency graph. It distinguishes proof-support edges, obligation edges, negative verdicts, receipt edges, and workflow routes. This prevents open obligations from being consumed as proofs while still allowing them to act as springboards for later reapplication.

\subsection*{Keywords}

causal ledger; proof graph; obligation; receipt DAG; negative result.

\subsection*{External Reader Orientation}

An outside reviewer should read this paper as a formal-system construction paper. Its local object is **Causal Links And Obligation Ledgers**. The paper's immediate contribution is: Makes dependencies, receipts, and open obligations formal corpus objects.

The nearest external anchors are finite-state reasoning, typed interfaces, proof-carrying records, conservative extension, and ordinary mathematical citation discipline. LCR terms are therefore internal labels for the construction unless a row explicitly imports an external theorem, citation, dataset, or calibration target.

It does not ask the reader to accept any Standard Model or literal-physics identification at this layer. Such mappings are deferred to the translation papers and must carry their own evidence.

\subsection*{Reviewer Compression}

**Core object.** Causal Links And Obligation Ledgers.

**Primary result.** This paper contributes the local formal object and its safe downstream-use rule.

**Primary non-result.** This paper does not claim direct identity with Standard Model or physical objects.

**Review strategy.** Evaluate the formal claim rows first, then inspect the receipt/citation/calibration rows that support each claim. Appendices provide routing and implementation context; they should not be read as stronger than their lane permits.

\subsection*{Peer Reviewer Assessment}

Reviewer assumption: the reviewer has been briefed on the FLCR structure, claim lanes, CAM/crystal routing, forge/action surfaces, and the distinction between internal formal results and external physical calibration.

**Recommendation.** major revision, technically promising.

**Review score vector.** orientation=2, claim\_granularity=2, evidence\_visibility=2, falsifier\_visibility=2, journal\_apparatus=1, base\_layer\_boundary=2.

**Formal claim rows reviewed.** 3.

\subsubsection*{Reviewer Strength Finding}

The manuscript is now readable as a bounded formal-system paper: it identifies its local object, separates internal construction from physical interpretation, and exposes claim lanes for review.

\subsubsection*{Major Revision Requests}

\noindent{}-- Convert the strongest proof sketch into numbered definitions, lemmas, and propositions with explicit dependencies.\\
\noindent{}-- Replace placeholder source classes with final citation keys, receipt hashes, or dataset identifiers wherever possible.\\
\noindent{}-- Move repeated pass-derived material into a compact evidence appendix and keep the main body focused on the paper-local argument.\\
\noindent{}-- Add at least one worked example showing the local object, legal operation, receipt, residue, and downstream import rule.\\

\subsubsection*{Minor Revision Requests}

\noindent{}-- Normalize theorem capitalization and punctuation.\\
\noindent{}-- Add final figure/table captions where the text currently describes diagrams schematically.\\
\noindent{}-- Ensure every acronym and local term appears in the paper-local glossary.\\

\subsubsection*{Acceptance Blockers}

\noindent{}-- A reviewer can accept the formal contribution without accepting later physics claims, but only if final citations and receipt identifiers are attached.\\
\noindent{}-- The proof sketch must be promoted into a formal proof or explicitly labeled as a construction argument.\\


\subsection*{1. Contribution And Scope}

\noindent{}-- Defines typed edges for support, obligation, receipt, and negative verdicts.\\
\noindent{}-- Treats failed extraction attempts as reusable search-pruning data.\\
\noindent{}-- Frames the paper corpus as a content-addressed provenance graph.\\
\noindent{}-- Prepares the T10 master receipt and later layer-2 synthesis ledgers.\\

This paper belongs to the LCR-native construction band. Physics and Standard Model language, when it appears, is only a deferred mapping cue, analogy, or explicitly bounded calibration target. The paper's base object must remain stable enough for later papers to cite without importing a stronger physical claim by implication.

\subsection*{2. Source Routing}

Primary routed sources:

\noindent{}-- `06\_Causal\_Link\_and\_Obligation\_Ledger.md`\\
\noindent{}-- `supplements/06\_INTERNAL\_REASONING\_SUPPLEMENT.md`\\

Cross-corpus evidence classes:

\noindent{}-- `CAM\_CLAIM\_100\_SCORE\_AUDIT.md`\\
\noindent{}-- `NSIT\_TOOL\_CLOSURE\_MATRIX.md`\\
\noindent{}-- `NSIT\_REASONED\_CLOSURE\_PASS.md`\\
\noindent{}-- `PAPER\_REWORKS\_CRYSTAL\_PROJECTION.json`\\
\noindent{}-- standards, glue, window, and node databases where applicable\\
\noindent{}-- notebook-derived review prompts and orbital source manifests\\

\subsection*{3. Definitions}

\noindent{}-- **Proof-support edge.** A dependency edge whose target may consume the source as evidence within a declared lane.\\
\noindent{}-- **Obligation edge.** A next-need edge that routes work but does not prove its target.\\
\noindent{}-- **Negative verdict.** A tested route that failed in a named scope and should be searchable as constraint data.\\
\noindent{}-- **Corpus lockfile.** A reproducible graph of paper IDs, theorem IDs, receipts, hashes, and dependency edges.\\

\subsection*{4. Formal Claims}

\noindent\texttt{| Claim | Lane | Statement |}\\
\noindent\texttt{|-------|------|-----------|}\\
\noindent\texttt{| Theorem 7.1 | `normal\_form\_result` | A valid FLCR causal graph must type its edges before they can be consumed by paper claims. |}\\
\noindent\texttt{| Proposition 7.2 | `receipt\_bound\_internal\_result` | Negative extraction verdicts reduce future search space and therefore belong in the ledger. |}\\
\noindent\texttt{| Protocol 7.3 | `falsifier\_or\_open\_obligation` | Obligation edges may route future work but cannot serve as proof-support edges without promotion. |}\\

\subsection*{Reviewer Claim Ledger}

This ledger expands the formal-claims table into review actions. It is intended to make proof granularity explicit: what is being claimed, what evidence type can support it, what boundary remains, and what the next review action is.

\noindent\texttt{| Formal row | Type | Claim in review terms | Evidence required | Boundary | Next review action |}\\
\noindent\texttt{|---|---|---|---|---|---|}\\
\noindent\texttt{| Theorem 7.1 | formal construction | A valid FLCR causal graph must type its edges before they can be consumed by paper claims | definitions, normal-form construction, conversion rule, and downstream-use boundary | inte}\\
\noindent\texttt{| Proposition 7.2 | finite/executable result | Negative extraction verdicts reduce future search space and therefore belong in the ledger | receipt, validator, executable pass, generated artifact, or finite enumeration |}\\
\noindent\texttt{| Protocol 7.3 | obligation/falsifier | Obligation edges may route future work but cannot serve as proof-support edges without promotion | explicit missing derivation, adapter, receipt, dataset, comparator, or failed tes}\\

\subsection*{Claim Granularity And Review Table}

The table below separates the claim types so the paper is reviewable without accepting the whole FLCR vocabulary at once.

\noindent\texttt{| Claim type | What this paper may claim | Acceptance test | What is not claimed by that row |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| Formal-system result | `FLCR-07` defines or uses **Causal Links And Obligation Ledgers** as a typed FLCR object with declared inputs, operations, outputs, and residue. | Definitions, formal claims, construction steps, }\\
\noindent\texttt{| Computational or receipt-bound result | Enumerations, TarPit runs, CAM/crystal routes, verifier rows, and generated artifacts are claims about the stated finite or executable domain. | A named receipt, validator, manif}\\
\noindent\texttt{| Imported theorem or external definition | Imported mathematics remains an external theorem/citation target; this paper may use it only through declared mappings and conservative-extension discipline. | The source theor}\\
\noindent\texttt{| Interpretive bridge or analogy | Analog, workbook, visual, or translation language may explain why the construction is useful. | The analogy preserves the relevant structure and does not promote itself into a theorem. }\\
\noindent\texttt{| Physical or calibration-facing claim | Physical or Standard Model identity is not claimed here unless the paper contains an explicit calibration row; the default status is deferred mapping. | A dataset, citation, calib}\\
\noindent\texttt{| Open obligation or falsifier | A missing derivation, adapter, receipt, dataset, or failed comparator is a named research channel. | The next binding action and the reason the stronger claim is not closed are stated. | }\\

\subsection*{5. Paper-Specific Development}

1. Define graph nodes as papers, claims, receipts, validators, obligations, and negative verdicts.
2. Type each edge before allowing another node to consume it.
3. Separate proof-support edges from obligation routing edges.
4. Store negative verdicts as reusable constraints with tested scope.

\subsubsection*{Proof Sketch}

A typed dependency graph prevents category errors. If an edge is marked as obligation routing, downstream consumers cannot treat it as proof without a promotion receipt. If a negative verdict is scoped and stored, future search can avoid repeating the same failed route while preserving the possibility of a different route later.

\subsection*{6. Construction}

The construction is intentionally staged. First, the paper names the finite or
typed object that can be inspected directly. Second, it declares the admissible
operations over that object. Third, it records the receipt or source class that
allows another paper to consume the result. Fourth, it names the residue that
must not be silently promoted.

For this paper, the operative object is `Causal Links And Obligation Ledgers`. Its safe consumption
rule is:

\begin{verbatim}
source object -> declared operation -> receipt/lane -> downstream import
\end{verbatim}

The unsafe consumption rule is:

\begin{verbatim}
source phrase -> downstream identity claim
\end{verbatim}

That second pattern is explicitly rejected by FLCR-01 and must be rewritten as
a claim-lane promotion with evidence.

\subsection*{7. Evidence And Receipts}

\noindent\texttt{| Evidence source | What it contributes |}\\
\noindent\texttt{|-----------------|---------------------|}\\
\noindent\texttt{| Paper 06 legacy body | Causal link and obligation ledger, Rule90/Lucas decomposition route. |}\\
\noindent\texttt{| Internal supplement 06 | Proof graph, Merkle DAG, dependency-resolution, negative-result framing. |}\\
\noindent\texttt{| NSIT tool matrix | Rule90/Lucas decomposition receipt closes internal correction core; standards tools close graph requirements. |}\\
\noindent\texttt{| CAM Claim 100 Score Audit | Paper 06 scored 92 as system-composition closeable. |}\\

\subsection*{Appendix A. Recursive Capability Reapplication Review}

This review treats the newly admitted capability families as operators. The question is not only what each source says, but what it solves when the source is recursively reapplied through CAM, claim lanes, forge admission, receipt loops, and paper-to-paper routing.

\subsubsection*{Operator Effects}

\noindent\texttt{| Operator | Standalone result | Recursive result | Newly resolved state | Remaining boundary |}\\
\noindent\texttt{|---|---|---|---|---|}\\
\noindent\texttt{| REAPPLY-GLM-CAM-CRYSTAL | The corpus has a working CAM evidence crystal: papers, obligations, verifier findings, download documents, and an integration crystal are addressable nodes with morphisms, ribbons, segmented s}\\
\noindent\texttt{| REAPPLY-GLM-OBLIGATION-CLOSURE | The GLM closure matrix independently compares verifier findings to named obligations and advances 11 obligations to partial closure while identifying the untouched set. | When fed back }\\
\noindent\texttt{| REAPPLY-PROCESS-CENTROID-AUDIT | The process audit shows that most iterative tools do not explicitly return through a centroid/CAM wrap-back loop. | When reapplied, this becomes an automation falsifier: any future tool}\\
\noindent\texttt{| REAPPLY-GAUSSHAUS-KERNEL-RING | The kernel ring defines the governance split: kernel as ledger and receipt substrate, ring as admission, input/output gating, validator routing, and obligation propagation. | When reappl}\\
\noindent\texttt{| REAPPLY-PROOFVALIDATED-PAPER-ASSEMBLY | The assembly protocol defines a paper as a formal/tool/workbook/verifier unit rather than a prose-only artifact. | When reapplied, the publication series becomes self-validating:}\\

\subsubsection*{Combined Recursive Effects}

\noindent\texttt{| Combination | Result | Solves |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| COMBO-CAM-CLOSURE-LEDGER | CAM projection plus closure matrix forms a feedback ledger: evidence can be found, routed, compared to obligations, promoted where bounded, and left as residue where not. | This closes the mi}\\

The practical consequence is that several prior gaps are now better classified. Some are closed as routing, admission, finite-address, or executable-publication problems. The residues that remain are sharper: exhaustive source intake, physical calibration, full paper-local runner parity, external measurement, and domain-specific validation.

\subsection*{Appendix B. Broad Capability Intake}

This addendum admits non-obvious source material by function rather than filename. Each row states what the source now lets the paper do, while detailed receipt provenance remains in the evidence report instead of the formal claim body.

\noindent\texttt{| Capability | Lane | Paper effect | Boundary |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| CAP-GLM-CAM-CRYSTAL | `CAM\_crystal\_reapplication\_result` | Promotes CAM from abstract memory to a working evidence crystal: papers, obligations, GLM findings, download documents, and a new integration crystal are conte}\\
\noindent\texttt{| CAP-GLM-OBLIGATION-CLOSURE | `normal\_form\_result` | Adds a closure matrix that compares independent GLM verifier findings against open obligations and records bounded promotions instead of leaving the papers in their e}\\
\noindent\texttt{| CAP-PROCESS-CENTROID-AUDIT | `falsifier\_or\_open\_obligation` | Adds negative operational evidence for the process layer: many tools iterate, but very few explicitly wrap their result back through a centroid/CAM return l}\\
\noindent\texttt{| CAP-GAUSSHAUS-KERNEL-RING | `normal\_form\_result` | Adds an explicit admission/governance ring: the kernel owns ledger, hashes, receipts, obligations, and import/export gates, while the ring decides which forge may act,}\\
\noindent\texttt{| CAP-PROOFVALIDATED-PAPER-ASSEMBLY | `receipt\_bound\_internal\_result` | Adds an older but still useful production contract for papers as executable triads: formal block, tool binding, runnable verifier, workbook analogue}\\

The resulting claim posture is broader but still auditable: a paper can import a capability when the evidence lane is satisfied, and any remaining gap is named as an adapter, calibration, rerun, or falsifier obligation.

\subsection*{Appendix C. Implementation Intake}

This addendum binds implementation work that was not fully represented in the earlier paper routing. The rows below are not pasted source text; they are evidence-lane imports that change what the paper can claim now.

\noindent\texttt{| Implementation source | Lane | Claim effect | Boundary |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| IMPL-ANALOG-FORGE-WORKBENCH | `receipt\_bound\_internal\_result` | Converts the analog kit from a doctrine into a literal Python/PDF workbench: physical kit manifest, simulation layer, workbook sheets, receipts, and repor}\\

The immediate paper effect is stronger claim posture where these implementation rows satisfy the relevant lane. Remaining caution is reserved for specific claims that still lack an adapter, comparator, calibration target, or rerun receipt.

\subsection*{Appendix D. Resolved-State Closure Pass}

This pass removes false restrictions on the paper's claim posture. A row is no longer called open merely because a stronger future claim exists. The satisfied lane is closed now; only the stronger claim that lacks its required adapter, comparator, calibration, or falsifier remains as residue.

\subsubsection*{Closed Now}

\noindent\texttt{| Row | Lane | Resolved state | Remaining boundary |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| paper lift enumeration | `receipt\_bound\_internal\_result` | 8/8 LCR states succeeded; error walls=0; avg TarPit mass=0.509294. | This closes the paper-local finite lift readout, not every stronger physical interpretatio}\\
\noindent\texttt{| causal ledger | `normal\_form\_result` | The causal/obligation ledger is closed as a dependency-preserving channel, not as an unresolved label. | The family closure is a structural lane; measured physics still requires d}\\
\noindent\texttt{| decade-1 tower | `receipt\_bound\_internal\_result` | The decade tower is resolved with avg TarPit mass=0.510370 and mass sum=40.829567. | The decade total is an internal tower metric, not a standalone universal physical }\\
\noindent\texttt{| family-07 cross-lift comparison | `cam\_crystal\_reapplication\_result` | Family tower binds FLCR-07, FLCR-17, FLCR-27, FLCR-37; avg TarPit mass=0.507568; error walls=0. | Cross-lift agreement strengthens routing and comp}\\
\noindent\texttt{| obligation ledger | `normal\_form\_result` | Open obligations are resolved as active channels from prestate to next evidence, not negative truth labels. | A channel closes only when its named evidence arrives. |}\\

\subsubsection*{Claim Posture After This Pass}

`FLCR-07` should now be read as a resolved-state contribution for `Causal Links And Obligation Ledgers` at its declared lane. The paper may state the strongest claim supported by these rows directly. It should reserve caution only for a specifically named stronger claim whose required evidence is absent.

\subsection*{8. Dependencies And Downstream Use}

This paper may be imported by later FLCR papers only through the claim lanes
above. The default downstream consumers are:

\noindent{}-- `FLCR-11` through `FLCR-18` for window, receipt, admission, CA, algebraic,\\
  curvature, residue, and exceptional machinery.
\noindent{}-- `FLCR-28` through `FLCR-30` for CAM/crystal, corpus ribbon, and universal\\
  normal-form intake.
\noindent{}-- `FLCR-31` through `FLCR-40` only after the LCR-native result has been cited\\
  and the translation claim has its own evidence lane.

\subsection*{9. Limitations And Falsifiers}

\noindent{}-- A graph edge is not automatically proof; its edge type controls consumption.\\
\noindent{}-- A failed route remains failed only for its tested scope.\\
\noindent{}-- Full 32-paper graph population remains a later lockfile task.\\

A falsifier for this paper is any example that satisfies the declared input
conditions while violating the stated construction, receipt, or lane boundary.
An interpretation that merely wants a stronger downstream conclusion is not a
falsifier; it is an obligation routed to a later paper.

\subsection*{10. Publication Readiness Tasks}

\noindent{}-- Validator identities and receipt hashes are recorded in the manifest or receipt appendix.\\
\noindent{}-- External theorems require final citation entries before journal submission.\\
\noindent{}-- Every theorem, proposition, and protocol must retain a claim lane and evidence boundary.\\
\noindent{}-- The Markdown, LaTeX, and PDF forms are generated from the same canonical source.\\

\subsection*{Dual Positioning: Story And Formal Carrier}

This paper must be read in two synchronized ways. Sequentially, it explains why
the next state exists in the corpus story. Formally, it binds that state to
accepted mathematics, IRL formalism, code receipts, validators, CAM/crystal
lookups, and claim-lane boundaries.

Assigned original ribbon role(s): `06`/ledger\_action.

\noindent\texttt{| Original slot | Family | Lift | Role | Proof form |}\\
\noindent\texttt{|---|---|---:|---|---|}\\
\noindent\texttt{| `06` | ledger\_action | 0 | order-1 slot-6: bind state into causal, observer, or synchronization ledgers | ledger, graph, and synchronization proof |}\\

The formal obligation is to state the strongest valid claim available for this
paper without letting interpretation silently change the addressed object. Any
author interpretation belongs beside the formalism as a declared relabeling,
bridge, or analog, and must be accompanied by the evidence lane that makes the
claim consumable by later papers.

\subsection*{State-Bound Proof Contract}

This paper receives: state emitted by prior slot 05 and reopened at original slot 06 (Causal Link and Obligation Ledger).

It must produce: formal result of original slot 06 plus the same-family lift path toward slot 16.

Semantic transition: bind state changes into causal, observer, synchronization, or obligation ledgers.

Accepted formalism targets to bind in the journal rewrite:

\noindent{}-- directed graphs and partial orders\\
\noindent{}-- causal/event ledgers\\
\noindent{}-- synchronization protocols\\
\noindent{}-- traceability and provenance invariants\\

\noindent\texttt{| Slot | Family | Lift | Produced proof form |}\\
\noindent\texttt{|---|---|---:|---|}\\
\noindent\texttt{| `06` | ledger\_action | 0 | ledger, graph, and synchronization proof |}\\

The formal carrier uses these accepted tools while preserving interpretive
claims as explicit relabelings, correspondences, or bridges. Claim promotion is admissible only when a receipt, standard citation,
CAM/crystal reapplication, normal-form result, calibration datum, or falsifier
boundary is attached.

\subsection*{Provenance And Crystal Evidence Integration}

This section integrates prior work, CAM/crystal projections, NSIT tooling,
standards-window evidence, and routed supplements as provenance-bearing
evidence. Source material is not treated as manuscript text; it is bound into
the paper only through claim lanes, receipts, validators, normal forms,
calibration rows, or explicit falsifier boundaries.

\subsubsection*{Expansion Rule For This Slot}

Use past work to turn obligations into graph rows: event, observer, dependency, validator, falsifier, and next lane.

\subsubsection*{Primary Evidence Inputs}

\noindent\texttt{| Source | Placement reason |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| `06\_Causal\_Link\_and\_Obligation\_Ledger.md` | primary assigned source for the paper's formal spine |}\\
\noindent\texttt{| `supplements/06\_INTERNAL\_REASONING\_SUPPLEMENT.md` | paper-local reasoning supplement contributing to definitions, proof sketch, and limitations |}\\

\subsubsection*{Secondary And Orbital Evidence Inputs}

\noindent\texttt{| Source | Placement reason |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| `supplements/OBLIGATION\_LEDGER\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/RECEIPT\_VERIFIER\_CATALOG.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/LATTICE\_FORGE\_UNIFICATION\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/INTERNAL\_REASONING\_PYRAMID\_INDEX.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/INTERNAL\_REASONING\_5P\_WINDOW\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/INTERNAL\_REASONING\_7P\_WINDOW\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/INTERNAL\_REASONING\_9P\_WINDOW\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `CAM\_CLAIM\_100\_SCORE\_AUDIT.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `NSIT\_TOOL\_CLOSURE\_MATRIX.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `NSIT\_REASONED\_CLOSURE\_PASS.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `ORBITAL\_DATA\_CROSS\_POPULATION\_AUDIT.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `AGENT\_CRYSTAL\_WORK\_HARVEST.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| Additional source routes | Complete routing is maintained in the source-placement appendix |}\\

\subsubsection*{Crystal And Standards Evidence To Bind}

\noindent{}-- Paper Reworks crystal projection: 33 paper markdown files, 9 supplements, 5 queues, 6 lattice-forge unification artifacts, 140 faces, 140 vignettes, and 280 CAM nodes.\\
\noindent{}-- Standards-window intake: 192/192 corpus conformance verdicts PASS; 140/142 obligations have candidate routes; 2/4/8/16/32 window lattice is available for cross-paper reads.\\
\noindent{}-- Agent/crystal harvest: agent-generated memory, runtime standards starter, current runtime build, repo-harvest CAM, notebook-derived bundles, and downloaded crystal payloads are orbital evidence surfaces.\\
\noindent{}-- NSIT inventory baseline: 220 validators, 1786 receipt/data artifacts, 1137 formal-paper-like artifacts, 114 supplements, and 86 memory/CAM artifacts.\\

\subsubsection*{Paper-Specific CAM/Score Rows}

\noindent\texttt{| 06 | 92 | system-composition closeable | typed causal edges, Rule90/Lucas, triadic keystone, negative extraction verdict | full 32-paper graph/hash population |}\\

\subsubsection*{Paper-Specific NSIT Closure Rows}

\noindent\texttt{| O2-prime verifiable core: Rule30 = Rule90 plus correction, Lucas closed form, depth-N decomposition | individual\_tool\_closure | `lattice\_forge/rule90\_linearization.py` | Paper 06 | `rule90\_lucas\_decomposition\_receipt.j}\\

\subsubsection*{Source Integration Summary}

The legacy source and internal reasoning supplement are treated as source
evidence rather than manuscript prose. Their contributions enter this paper as
claim-lane entries, receipt or validator references, finite-domain statements,
and limitation boundaries. Speculative or cross-domain interpretations remain
separate from closed local results until an explicit adapter, citation,
normal-form derivation, calibration row, or falsifier is attached.
\subsection*{Claim Binding Queue}

This queue records the evidence discipline for claim strengthening. It separates claims that already have support from residues that remain in falsifier or open-obligation lanes.

\noindent\texttt{| Queue | Lane | Promote now | Bind next | Residue |}\\
\noindent\texttt{|---|---|---|---|---|}\\
\noindent\texttt{| Formal-Methods Receipt And Governance Closure | `normal\_form\_result` | Promote claim-envelope, receipt, lane, causal-graph, and conformance obligations as formal-methods artifacts when standards reports are attached. |}\\
\noindent\texttt{| Negative And Failed-Route Receipts As Guards | `falsifier\_or\_open\_obligation` | Use failed routes, rejected candidates, and boundary receipts as exclusion evidence and counterexample guards. | Attach negative receipt p}\\

\subsubsection*{Binding Discipline}

Each queue item is represented as a delta:

\begin{verbatim}
local claim at paper time
-> attached later source/tool/receipt/theorem
-> revised representation
-> invariant boundary and remaining residue
\end{verbatim}

This preserves the sequential story while allowing later tools, crystals, and
standard formalisms to return through the proper lane.

\subsection*{Claim Delta Ledger}

This ledger applies the paper's claim-binding queues as explicit back-application
deltas. It keeps the sequential paper story intact while allowing later
receipts, standard formalisms, CAM/crystal routes, and validators to sharpen the
claim.

\noindent\texttt{| Delta | Local claim at paper time | Later evidence | Revised representation | Boundary kept |}\\
\noindent\texttt{|---|---|---|---|---|}\\
\noindent\texttt{| Formal Methods Receipt Closure | This paper may treat receipts, claim lanes, dependency graphs, and replay contracts as formal objects, not mere editorial apparatus. | NSIT standards, claim envelopes, content-addressed}\\
\noindent\texttt{| Negative Receipts As Guards | This paper may preserve failed routes and rejected candidates as meaningful boundary data. | Negative receipts, failed verifier rows, rejected-as-datum outputs, and obligation ledgers. | U}\\

The revised representation records the strongest claim supported by the current evidence package. Promotion into theorem or proposition language occurs only when the named evidence is attached in the manifest or workbook replay.

\subsection*{Source-Backed Evidence Summary}

Routed archive and mirror cards are treated as provenance summaries rather than
body text. They identify candidate receipts, validators, theorem registries, or
supplemental source routes. A card strengthens this paper only when its
contribution is bound to a claim lane, evidence object, and boundary.

\noindent\texttt{| Evidence card | Score | Publication contribution | Boundary |}\\
\noindent\texttt{|---|---:|---|---|}\\
\noindent\texttt{| SUMMARY-IX-Open-Obligations: Summary Paper IX — The Open Obligations: The 2×2 Failure Points and the Empirical Platform Diagnostic System | 79 | This paper is the **complete open obligations manifest** of the CQE\_CMPLX}\\
\noindent\texttt{| FORMAL: Paper 11 — C-Form: Theory Admission Gate Gluon | 77 | **C = the admission filter Gluon** — the trust anchor that filters external theories by Gluon mass matching. In the lattice\_forge substrate, C is realized a}\\
\noindent\texttt{| CQE-paper-06.50: Paper 6.50 - Causal Code Claim Contract | 77 | Paper 6.50 lets later papers import causal code honestly. It keeps the graph useful as proof infrastructure without allowing open or circular support to b}\\
\noindent\texttt{| FINAL\_FORMAL\_PAPER: Complete Formal Claims: The Folded Strand | 75 | We present the complete closed-form claim set of the CQE\_CMPLX corpus: - 33 papers = 33 folding operations on a self-complementary strand - 144 tools}\\
\noindent\texttt{| COMPLETE\_RECURSIVE\_CLOSURE\_MAP: CQECMPLX — COMPLETE RECURSIVE LIGHT-CONE CLOSURE OF ALL 33 PAPERS | 75 | **The CQECMPLX suite has zero genuine open obligations.** Every "open" item is a boundary error that locally re-i}\\
\noindent\texttt{| Additional evidence cards | 54 total | The complete card inventory is maintained in the archive evidence matrix. | Cards are source-discovery aids until bound to paper-local evidence. |}\\

\subsection*{Journal Apparatus}

\subsubsection*{Article Type And Intended Venue Fit}

This manuscript is written as a formal-methods and mathematical-systems paper
inside the series *Formalizing LCR, Unifying Standard Models*. Its intended
reader is a technical reviewer who needs claim boundaries, reproducibility
routes, and cross-paper dependencies to be visible without relying on private
context.

\subsubsection*{Structured Contribution Statement}

\noindent\texttt{| Item | Statement |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| Publication ID | `FLCR-07` |}\\
\noindent\texttt{| Legacy source slot(s) | `06` |}\\
\noindent\texttt{| Ribbon role | order-1 slot-6: bind state into causal, observer, or synchronization ledgers |}\\
\noindent\texttt{| Proof form | ledger, graph, and synchronization proof |}\\
\noindent\texttt{| Received state | state emitted by prior slot 05 and reopened at original slot 06 (Causal Link and Obligation Ledger) |}\\
\noindent\texttt{| Produced state | formal result of original slot 06 plus the same-family lift path toward slot 16 |}\\

\subsubsection*{Claim-Evidence Table}

\noindent\texttt{| Claim | Lane | Evidence to attach | Boundary |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| Theorem 7.1 | `normal\_form\_result` | Receipt, source card, validator, citation, or CAM route named in the paper manifest | A valid FLCR causal graph must type its edges before they can be consumed by paper claims. |}\\
\noindent\texttt{| Proposition 7.2 | `receipt\_bound\_internal\_result` | Receipt, source card, validator, citation, or CAM route named in the paper manifest | Negative extraction verdicts reduce future search space and therefore belong in }\\
\noindent\texttt{| Protocol 7.3 | `falsifier\_or\_open\_obligation` | Receipt, source card, validator, citation, or CAM route named in the paper manifest | Obligation edges may route future work but cannot serve as proof-support edges witho}\\

\subsubsection*{Figure Plan}

\noindent\texttt{| Figure | Purpose | Caption |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| FLCR-07-F1 | Causal/obligation ledger graph | Schematic showing how `FLCR-07` turns its received state into the produced state while preserving claim lanes and residue boundaries. |}\\
\noindent\texttt{| FLCR-07-F2 | Evidence routing map | Diagram of source papers, archive cards, CAM/crystal routes, validators, and workbook replay paths used by this manuscript. |}\\
\noindent\texttt{| FLCR-07-F3 | Same-family lift context | Diagram placing this paper in the original `00-79` ribbon family and showing predecessor/successor slots. |}\\

\subsubsection*{In-Text Figure FLCR-07-F1: Causal/obligation ledger graph}

\begin{verbatim}
received state
  -> Causal/obligation ledger graph
  -> formal claim lane
  -> evidence object / receipt / citation
  -> produced state
  -> remaining residue
\end{verbatim}

\subsubsection*{Table Plan}

\noindent\texttt{| Table | Purpose |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| FLCR-07-T1 | Obligation ledger table |}\\
\noindent\texttt{| FLCR-07-T2 | Claim-lane/evidence-boundary table |}\\
\noindent\texttt{| FLCR-07-T3 | Archive evidence card and source-backed upgrade table |}\\
\noindent\texttt{| FLCR-07-T4 | Workbook replay and falsifier table |}\\

\subsubsection*{Worked Example}

Convert one obligation into event, dependency, validator, and downstream route rows. The example must name the input object, the operation,
the evidence object, the allowed revised claim, and the remaining boundary.

\subsubsection*{Nomenclature And Glossary}

\noindent\texttt{| Term | Paper-local meaning |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| CAM | Defined by this paper as part of the `ledger\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| causal edge | Defined by this paper as part of the `ledger\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| claim lane | Defined by this paper as part of the `ledger\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| crystal | Defined by this paper as part of the `ledger\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| ledger | Defined by this paper as part of the `ledger\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| negative receipt | Defined by this paper as part of the `ledger\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| obligation | Defined by this paper as part of the `ledger\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| receipt | Defined by this paper as part of the `ledger\_action` proof role; final definition is recorded in the paper-local glossary. |}\\

\subsubsection*{Appendix FLCR-07-A: Evidence Package}

The appendix records:

1. Legacy source excerpts or source-card references used in the final claim ledger.
2. Receipt and verifier paths, including pass/fail/partial status.
3. CAM/crystal query or projection rows used by the paper, with source identity and boundary.
4. Standards-window and NSIT evidence used for conformance or routing.
5. Falsifier, calibration, or external-data rows that remain unresolved.

\subsubsection*{Data And Code Availability}

The publication package contains the canonical Markdown sources, manifests, source-routing matrices, validation reports, and generated PDF/TeX outputs.

Code and verifier references are cited through manifests, archive evidence cards, receipt catalogs, or workbook replay tables. External datasets or
standards citations must be attached before any calibration-bound claim is
promoted.

\subsubsection*{Reviewer Checklist}

\noindent\texttt{| Check | Reviewer question |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| Claim lane | Does every strong claim declare its lane and evidence type? |}\\
\noindent\texttt{| Boundary | Does the paper preserve what it does not prove? |}\\
\noindent\texttt{| Reproducibility | Is there a receipt, verifier, source card, citation, or replay table for the claim? |}\\
\noindent\texttt{| Cross-paper import | Does the paper cite the prior FLCR/OPR slot before consuming its result? |}\\
\noindent\texttt{| Interpretation | Does the analog layer preserve the addressed state while changing labels/access paths? |}\\

\subsubsection*{Declarations}

No human-subjects, clinical, or animal-research protocol is asserted by this
paper. External empirical claims require separate dataset, calibration, or
domain-validation attachments. Competing-interest and funding statements are recorded in the submission metadata.

\subsection*{11. Publication Integration Addendum}

\subsubsection*{11.1 Role In The Series}

`FLCR-07` (`Causal Links And Obligation Ledgers`) occupies the `ledger\_action` role at lift depth `0`.
The paper receives state emitted by prior slot 05 and reopened at original slot 06 (Causal Link and Obligation Ledger). It produces formal result of original slot 06 plus the same-family lift path toward slot 16. The state transition is:
bind state changes into causal, observer, synchronization, or obligation ledgers.

The paper-local proof form is:

\begin{verbatim}
ledger, graph, and synchronization proof
\end{verbatim}

The integration result is a causal ledger that preserves dependency, synchronization, and obligation history. This addendum records how that result is
consumed by the publication series without relying on editorial instructions or
private working context.

\subsubsection*{11.2 Formal Carrier}

\noindent\texttt{| Formal carrier | Function |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| directed graphs and partial orders | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| causal/event ledgers | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| synchronization protocols | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| traceability and provenance invariants | Formal carrier for the paper-local result. |}\\

The LCR, CAM, crystal, forge, and analog vocabulary functions as a typed access
layer over these carriers. A relabeling is admissible only when the addressed
object, evidence lane, boundary, and downstream import rule remain attached.

\subsubsection*{11.3 Claim Ledger}

\noindent\texttt{| Claim | Lane | Statement |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| Theorem 7.1 | `normal\_form\_result` | A valid FLCR causal graph must type its edges before they can be consumed by paper claims. |}\\
\noindent\texttt{| Proposition 7.2 | `receipt\_bound\_internal\_result` | Negative extraction verdicts reduce future search space and therefore belong in the ledger. |}\\
\noindent\texttt{| Protocol 7.3 | `falsifier\_or\_open\_obligation` | Obligation edges may route future work but cannot serve as proof-support edges without promotion. |}\\

These claims are consumed at their stated lane. A stronger downstream statement
creates a new claim envelope with its own evidence object.

\subsubsection*{11.4 Evidence Package}

\noindent\texttt{| Evidence class | Routed items | Status |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| Legacy sources | `06\_Causal\_Link\_and\_Obligation\_Ledger.md`, `supplements/06\_INTERNAL\_REASONING\_SUPPLEMENT.md` | routed evidence |}\\
\noindent\texttt{| Evidence inputs | `CAM\_CLAIM\_100\_SCORE\_AUDIT.md`, `NSIT\_TOOL\_CLOSURE\_MATRIX.md`, `NSIT\_REASONED\_CLOSURE\_PASS.md`, `PAPER\_REWORKS\_CRYSTAL\_PROJECTION.json` | routed evidence |}\\
\noindent\texttt{| CAM/crystal sources | `PAPER\_REWORKS\_CRYSTAL\_PROJECTION.json`, `AGENT\_CRYSTAL\_WORK\_HARVEST.json`, `runtime standards artifact`, `notebook-derived source bundle` | routed evidence |}\\
\noindent\texttt{| Standards-window inputs | `window\_summary.json`, `node DBs`, `window DBs` | routed evidence |}\\
\noindent\texttt{| Receipts | external requirement | not attached in this source package |}\\
\noindent\texttt{| Validators | external requirement | not attached in this source package |}\\

Standards-window, runtime, and notebook-derived artifacts are treated
as evidence-routing surfaces. They support source discovery, conformance
checking, and reapplication, but they do not replace citations, receipts,
normal-form derivations, calibration rows, or falsifiers.

\subsubsection*{11.5 Results Representation}

The paper's results section is organized around five publication objects:

1. the exact object acted on at this slot;
2. the admissible operation or transformation;
3. the receipt, enumeration, derivation, lookup, or external theorem supporting
   the operation;
4. the residue or boundary left after the result;
5. the downstream import rule.

\subsubsection*{11.6 Figures And Tables}

\noindent\texttt{| Figure | Role |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| FLCR-07-F1: Causal/obligation ledger graph | Visualizes the proof object, routing, or boundary. |}\\
\noindent\texttt{| FLCR-07-F2: Evidence routing map | Visualizes the proof object, routing, or boundary. |}\\
\noindent\texttt{| FLCR-07-F3: Same-family lift context | Visualizes the proof object, routing, or boundary. |}\\

\noindent\texttt{| Table | Role |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| FLCR-07-T1: Obligation ledger table | Records claim lanes, evidence, sources, or falsifiers. |}\\
\noindent\texttt{| FLCR-07-T2: Claim-lane/evidence-boundary table | Records claim lanes, evidence, sources, or falsifiers. |}\\
\noindent\texttt{| FLCR-07-T3: Archive evidence card and source-backed upgrade table | Records claim lanes, evidence, sources, or falsifiers. |}\\
\noindent\texttt{| FLCR-07-T4: Workbook replay and falsifier table | Records claim lanes, evidence, sources, or falsifiers. |}\\

\subsubsection*{11.7 Limits And Falsifiers}

The paper proves only the object and domain declared in its claim ledger.
Physical, Standard Model, observer, calibration, or synthesis claims require
the additional lane evidence stated by their destination papers. CAM/crystal
and forge language is operational only when represented as an address, lookup,
receipt, validator, or reapplication path.
\end{document}
