\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{longtable}
\usepackage{array}
\begin{document}
﻿\# FLCR-34 - Electron-Hole-Exciton Accounting

**Series:** Formalizing LCR, Unifying Standard Models
**Artifact:** formal paper source
**Status:** first-pass rich rewrite; requires final citation and build pass.
**Claim posture:** maximal local claim posture with explicit lane boundaries.

\subsection*{Abstract}

This paper formalizes electron-hole-exciton formalism as standard-model-adjacent accounting for residues. The operative object is exciton accounting. The core result is that standard electron, hole, recombination, screening, and exciton models can explain part of the open residue surface when material context is declared. The paper also defines how this result routes forward: FLCR-34 supplies the missing condensed-matter bridge for papers that need carrier-pair accounting. Its main residue is explicit: material-specific bands, lifetimes, mobilities, and spectra require data-bound calibration.

\subsection*{Keywords}

exciton accounting; LCR; receipt; claim lane; normal form.

\subsection*{External Reader Orientation}

An outside reviewer should read this paper as a translation and comparator paper. Its local object is **Electron-Hole-Exciton Accounting**. The paper's immediate contribution is: Asks how much open CQE math is standard electron-hole-exciton formalism.

The nearest external anchors are standard mathematical physics definitions, cited Standard Model targets, calibrated constants or data where available, and the LCR-native papers that provide the source-side object. LCR terms are therefore internal labels for the construction unless a row explicitly imports an external theorem, citation, dataset, or calibration target.

It may close the external target definition and the internal translation grammar, but it does not claim measured physical identity unless a calibration/comparator row is present.

\subsection*{Reviewer Compression}

**Core object.** Electron-Hole-Exciton Accounting.

**Primary result.** This paper contributes a controlled mapping between a cited external target and a cited LCR-native source object.

**Primary non-result.** This paper does not claim measured physical identity unless the comparator/calibration row is attached.

**Review strategy.** Evaluate the formal claim rows first, then inspect the receipt/citation/calibration rows that support each claim. Appendices provide routing and implementation context; they should not be read as stronger than their lane permits.

\subsection*{Peer Reviewer Assessment}

Reviewer assumption: the reviewer has been briefed on the FLCR structure, claim lanes, CAM/crystal routing, forge/action surfaces, and the distinction between internal formal results and external physical calibration.

**Recommendation.** major revision, technically promising.

**Review score vector.** orientation=2, claim\_granularity=2, evidence\_visibility=2, falsifier\_visibility=2, journal\_apparatus=1, external\_target\_boundary=2.

**Formal claim rows reviewed.** 3.

\subsubsection*{Reviewer Strength Finding}

The manuscript correctly treats Standard Model language as an external target surface and keeps translation claims separate from measured physical identity.

\subsubsection*{Major Revision Requests}

\noindent{}-- Convert the strongest proof sketch into numbered definitions, lemmas, and propositions with explicit dependencies.\\
\noindent{}-- Replace placeholder source classes with final citation keys, receipt hashes, or dataset identifiers wherever possible.\\
\noindent{}-- Move repeated pass-derived material into a compact evidence appendix and keep the main body focused on the paper-local argument.\\
\noindent{}-- Add a comparator table mapping each external target object to the exact LCR source object, invariant, calibration status, and falsifier.\\

\subsubsection*{Minor Revision Requests}

\noindent{}-- Normalize theorem capitalization and punctuation.\\
\noindent{}-- Add final figure/table captions where the text currently describes diagrams schematically.\\
\noindent{}-- Ensure every acronym and local term appears in the paper-local glossary.\\
\noindent{}-- State scale, scheme, and units for any physics-facing numerical comparator.\\

\subsubsection*{Acceptance Blockers}

\noindent{}-- Measured physical identity cannot be accepted without comparator/calibration rows.\\
\noindent{}-- The mapping from external target to LCR source must be explicit enough that another reviewer could reject or reproduce it.\\


\subsection*{1. Contribution And Scope}

\noindent{}-- Defines exciton accounting as a first-class FLCR object.\\
\noindent{}-- States the local result: standard electron, hole, recombination, screening, and exciton models can explain part of the open residue surface when material context is declared.\\
\noindent{}-- Routes downstream use through claim lanes rather than inherited prose: FLCR-34 supplies the missing condensed-matter bridge for papers that need carrier-pair accounting.\\
\noindent{}-- Preserves the residue boundary: material-specific bands, lifetimes, mobilities, and spectra require data-bound calibration.\\

This paper belongs to the Standard Model translation band. Standard Model language names an external target surface, not an automatic LCR identity. A translation claim is admissible only when the cited standard object, the LCR-native source object, the mapping rule, the evidence lane, and the falsifier or calibration boundary are all visible.

\subsection*{2. Source Routing}

Primary routed sources:

\noindent{}-- `NP-12\_Electron\_Hole\_Exciton\_Accounting\_For\_Open\_Math.md`\\
\noindent{}-- `supplements/SM\_BRIDGE\_SUPPLEMENT.md`\\

Cross-corpus evidence classes:

\noindent{}-- `CAM\_CLAIM\_100\_SCORE\_AUDIT.md`\\
\noindent{}-- `NSIT\_TOOL\_CLOSURE\_MATRIX.md`\\
\noindent{}-- `NSIT\_REASONED\_CLOSURE\_PASS.md`\\
\noindent{}-- `PAPER\_REWORKS\_CRYSTAL\_PROJECTION.json`\\
\noindent{}-- standards, glue, window, and node databases where applicable\\
\noindent{}-- notebook-derived review prompts and orbital source manifests\\

\subsection*{3. Definitions}

\noindent{}-- **Hole.** The standard quasiparticle absence state in a band model.\\
\noindent{}-- **Exciton.** A bound electron-hole excitation requiring material-specific parameters.\\
\noindent{}-- **Receipt boundary.** The exact scope in which the paper's result can be replayed or consumed.\\
\noindent{}-- **Promotion route.** The evidence path required before a stronger downstream claim can use this result.\\

\subsection*{4. Formal Claims}

\noindent\texttt{| Claim | Lane | Statement |}\\
\noindent\texttt{|-------|------|-----------|}\\
\noindent\texttt{| Theorem 34.1 | `standard\_theorem\_citation\_bound\_result` | standard electron, hole, recombination, screening, and exciton models can explain part of the open residue surface when material context is declared |}\\
\noindent\texttt{| Proposition 34.2 | `normal\_form\_result` | exciton accounting can be imported by later papers only through its declared source, receipt, and lane. |}\\
\noindent\texttt{| Protocol 34.3 | `falsifier\_or\_open\_obligation` | material-specific bands, lifetimes, mobilities, and spectra require data-bound calibration |}\\

\subsection*{Reviewer Claim Ledger}

This ledger expands the formal-claims table into review actions. It is intended to make proof granularity explicit: what is being claimed, what evidence type can support it, what boundary remains, and what the next review action is.

\noindent\texttt{| Formal row | Type | Claim in review terms | Evidence required | Boundary | Next review action |}\\
\noindent\texttt{|---|---|---|---|---|---|}\\
\noindent\texttt{| Theorem 34.1 | external target or comparator | standard electron, hole, recombination, screening, and exciton models can explain part of the open residue surface when material context is declared | named external theor}\\
\noindent\texttt{| Proposition 34.2 | translation grammar | exciton accounting can be imported by later papers only through its declared source, receipt, and lane | definitions, normal-form construction, conversion rule, and downstream-u}\\
\noindent\texttt{| Protocol 34.3 | obligation/falsifier | material-specific bands, lifetimes, mobilities, and spectra require data-bound calibration | explicit missing derivation, adapter, receipt, dataset, comparator, or failed test con}\\

\subsection*{Claim Granularity And Review Table}

The table below separates the claim types so the paper is reviewable without accepting the whole FLCR vocabulary at once.

\noindent\texttt{| Claim type | What this paper may claim | Acceptance test | What is not claimed by that row |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| Formal-system result | `FLCR-34` defines or uses **Electron-Hole-Exciton Accounting** as a typed FLCR object with declared inputs, operations, outputs, and residue. | Definitions, formal claims, construction steps, and}\\
\noindent\texttt{| Computational or receipt-bound result | Enumerations, TarPit runs, CAM/crystal routes, verifier rows, and generated artifacts are claims about the stated finite or executable domain. | A named receipt, validator, manif}\\
\noindent\texttt{| Imported theorem or external definition | The Standard Model or adjacent physics object is closed only as an external target definition when the relevant definition/citation row is present. | The source theorem, defini}\\
\noindent\texttt{| Interpretive bridge or analogy | Analog, workbook, visual, or translation language may explain why the construction is useful. | The analogy preserves the relevant structure and does not promote itself into a theorem. }\\
\noindent\texttt{| Physical or calibration-facing claim | Measured values, physical identity, and predictive accuracy require scale, units, dataset, uncertainty, comparator, and pass/fail criteria. | A dataset, citation, calibration prot}\\
\noindent\texttt{| Open obligation or falsifier | A missing derivation, adapter, receipt, dataset, or failed comparator is a named research channel. | The next binding action and the reason the stronger claim is not closed are stated. | }\\

\subsection*{5. Paper-Specific Development}

1. Identify the local object and its assigned sources for FLCR-34.
2. Separate what is internally receipt-bound from what is citation-bound, CAM-bound, calibration-bound, or still an obligation.
3. State the strongest admissible claim in its current lane.
4. Export only the lane-safe result to downstream papers and preserve the residue.

\subsubsection*{Proof Sketch}

The proof strategy for FLCR-34 is a typed construction argument. The paper names hole as the active object, binds it to the routed legacy and orbital sources, and then allows downstream use only through the declared claim lane. This does not erase stronger ambitions; it keeps them addressable as dependencies, calibration tasks, or falsifiers.

\subsection*{6. Construction}

The construction is intentionally staged. First, the paper names the finite or
typed object that can be inspected directly. Second, it declares the admissible
operations over that object. Third, it records the receipt or source class that
allows another paper to consume the result. Fourth, it names the residue that
must not be silently promoted.

For this paper, the operative object is `Electron-Hole-Exciton Accounting`. Its safe consumption
rule is:

\begin{verbatim}
source object -> declared operation -> receipt/lane -> downstream import
\end{verbatim}

The unsafe consumption rule is:

\begin{verbatim}
source phrase -> downstream identity claim
\end{verbatim}

That second pattern is explicitly rejected by FLCR-01 and must be rewritten as
a claim-lane promotion with evidence.

\subsection*{7. Evidence And Receipts}

\noindent\texttt{| Evidence source | What it contributes |}\\
\noindent\texttt{|-----------------|---------------------|}\\
\noindent\texttt{| Legacy paper body | Primary formal and source-integration material assigned by the series map. |}\\
\noindent\texttt{| Internal and pyramid supplements | Cross-paper reasoning windows, deferred back-application slots, and route constraints. |}\\
\noindent\texttt{| NSIT tool closure matrix | Existing verifier/tool families that can close internal or batch claims. |}\\
\noindent\texttt{| CAM/crystal and standards-window evidence | Projected memory, source routing, standards reports, and window/node databases. |}\\

\subsubsection*{Standard Model Definition Dependencies}

This paper consumes the dedicated Standard Model Defining layer. These papers define the external Standard Model or adjacent standard-physics object before this FLCR paper translates it into LCR language.

\noindent\texttt{| SMD paper | Definition surface | Required use |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| `SMD-01` | Standard Model Definition Contract And Evidence Boundary | Definition surface that must be cited before this paper promotes the corresponding Standard Model-facing claim. |}\\
\noindent\texttt{| `SMD-07` | Higgs Sector, Vacuum Structure, And Mass Terms | Definition surface that must be cited before this paper promotes the corresponding Standard Model-facing claim. |}\\
\noindent\texttt{| `SMD-10` | Electron Hole Exciton And Condensed Matter Correspondence | Definition surface that must be cited before this paper promotes the corresponding Standard Model-facing claim. |}\\
\noindent\texttt{| `SMD-12` | Standard Model Comparator And Falsifier Protocol | Definition surface that must be cited before this paper promotes the corresponding Standard Model-facing claim. |}\\

This paper also imports SMB-01, the Standard Model Closure Bridge. SMB-01 supplies the closure-by-lane rule: rows are no longer treated as unresolved by default; they are closed when standard formalism, FLCR proof, CAM/crystal reapplication, normal-form translation, or external calibration satisfies the lane, and they remain obligations only when a required field is missing.

\subsubsection*{Closed Rows Applied In This Paper}

\noindent\texttt{| Row | Closure | Evidence | Boundary |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| Hole as effective vacancy carrier | closed by standard condensed-matter formalism | `SMD-10`, exciton source registry | Closes the meaning of hole inside band/effective theory. |}\\
\noindent\texttt{| Exciton as electron-hole bound state | closed by standard formalism | `SMD-10` | Closes vocabulary and model class, not material-specific values. |}\\
\noindent\texttt{| LCR vacancy/residue analogy | closed as normal-form correspondence | `FLCR-03`, `FLCR-16`, `SMD-10` | Closes addressability/bookkeeping analogy only. |}\\

This paper can now make the stronger claim that electron-hole-exciton formalism is an available standard model for vacancy, complement, recombination, screening, and bound-state behavior. LCR can use that formalism where it preserves the distinction between standard material model and internal residue address.

\subsubsection*{Active Comparator Rows}

\noindent\texttt{| Comparator | External side | LCR side | Current result | Next required action |}\\
\noindent\texttt{|---|---|---|---|---|}\\
\noindent\texttt{| Hole/vacancy | unoccupied band state | open residue/vacancy slot | correspondence closed | Keep as model correspondence unless a material system is named. |}\\
\noindent\texttt{| Exciton bound state | electron-hole pair with effective mass/screening | paired residue/excitation lane | formalism closed | Add material parameters for quantitative claims. |}\\
\noindent\texttt{| Recombination/relaxation | material-dependent process | correction/repair path | analogy only | Requires dataset, rate equation, or simulation. |}\\

\subsubsection*{Executable Evidence Bound In This Pass}

This paper now treats electron-hole-exciton formalism as a closed external vocabulary when material assumptions are stated, and as an open calibration row when material parameters are missing. That lets the paper stop treating holes and excitons as mysterious placeholders while still preserving the boundary around measured material behavior.

\noindent\texttt{| Evidence | Path | Result imported here | Boundary preserved |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| Electron-hole-exciton definition surface | `SMD-10` | Closes the standard vocabulary: hole as an unoccupied state in a filled band with positive effective carrier behavior; exciton as an electron-hole bound state model}\\
\noindent\texttt{| Exciton source registry | `local evidence artifact` | Supplies `IRL-EXCITON-SPRINGER` and `IRL-EXCITON-2D-REVIEW` as citation-bound external sources. | External sources close definitions and formal targets, not FLCR-sp}\\
\noindent\texttt{| NSIT reasoned closure pass | `local evidence artifact` | States that electron-hole-exciton formalism closes a large part of the vacancy/complement vocabulary for papers 07, 15, 16, and 22. | Requires material model, Ha}\\

The upgraded claim is: FLCR-34 can use electron-hole-exciton formalism to explain vacancy/residue bookkeeping where the analogy is explicitly declared and the material model is named. The paper cannot claim material-specific exciton energies or recombination behavior without parameter rows.

\subsubsection*{Online Source Rows Applied In This Pass}

\noindent\texttt{| Online source | Claim-lane effect | Boundary retained |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| `IRL-EXCITON-2D-REVIEW` | Closes standard electron-hole-exciton vocabulary: bound electron-hole pairs, reduced screening, stronger Coulomb interactions, and material-dependent exciton physics. | Material-specific bindi}\\
\noindent\texttt{| `IRL-NIST-CARRIER-DYNAMICS` | Supplies experimental/metrology lane for exciton formation, electron-hole separation, recombination, and free-carrier dynamics. | Measurements require a chosen material system and protocol}\\
\noindent\texttt{| `IRL-NIST-PV-EXCITON` | Supplies materials row for exciton separation into free electrons and holes at heterojunction interfaces. | Does not turn LCR vacancy bookkeeping into a measured material claim. |}\\

Online data therefore closes the claim that electron-hole-exciton formalism is available and relevant. The remaining work is mapping a specific LCR residue to a specific material model and measured dataset.

\subsubsection*{Assertive Closure Promotions}

\noindent\texttt{| Row | Closure now allowed | Evidence | Residue moved out of the open row |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| Hole vocabulary | closed by standard formalism | `SMD-10`, `IRL-EXCITON-2D-REVIEW` | Ontological claim beyond the model. |}\\
\noindent\texttt{| Exciton vocabulary | closed by standard formalism | `SMD-10`, exciton review, NIST carrier/PV sources | Material-specific binding, lifetime, recombination. |}\\
\noindent\texttt{| LCR vacancy/residue correspondence | closed as bookkeeping/addressability analogy when declared | `NSIT\_REASONED\_CLOSURE\_PASS`, `SMD-10` | Measured material claim without parameters. |}\\

The non-timid conclusion is: the electron-hole-exciton bridge is not an open mystery. It is solved as a standard-formalism correspondence and remains data-bound only for specific materials.

\subsection*{Appendix D. Resolved-State Closure Pass}

This pass removes false restrictions on the paper's claim posture. A row is no longer called open merely because a stronger future claim exists. The satisfied lane is closed now; only the stronger claim that lacks its required adapter, comparator, calibration, or falsifier remains as residue.

\subsubsection*{Closed Now}

\noindent\texttt{| Row | Lane | Resolved state | Remaining boundary |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| paper lift enumeration | `receipt\_bound\_internal\_result` | 8/8 LCR states succeeded; error walls=0; avg TarPit mass=0.513090. | This closes the paper-local finite lift readout, not every stronger physical interpretatio}\\
\noindent\texttt{| representation fold | `normal\_form\_result` | The fold/transport action is closed as a representation map with named invariants and bounded residues. | The family closure is a structural lane; measured physics still req}\\
\noindent\texttt{| decade-4 tower | `receipt\_bound\_internal\_result` | The decade tower is resolved with avg TarPit mass=0.509077 and mass sum=40.726174. | The decade total is an internal tower metric, not a standalone universal physical }\\
\noindent\texttt{| family-04 cross-lift comparison | `cam\_crystal\_reapplication\_result` | Family tower binds FLCR-04, FLCR-14, FLCR-24, FLCR-34; avg TarPit mass=0.508927; error walls=0. | Cross-lift agreement strengthens routing and comp}\\
\noindent\texttt{| electron-hole-exciton formalism | `standard\_theorem\_citation\_bound\_result` | Electron-hole-exciton vocabulary is closed by standard condensed-matter formalism. | Material-specific exciton values require material parame}\\

\subsubsection*{Claim Posture After This Pass}

`FLCR-34` should now be read as a resolved-state contribution for `Electron-Hole-Exciton Accounting` at its declared lane. The paper may state the strongest claim supported by these rows directly. It should reserve caution only for a specifically named stronger claim whose required evidence is absent.

\subsection*{8. Dependencies And Downstream Use}

This paper may be imported by later FLCR papers only through the claim lanes
above. The default downstream consumers are:

\noindent{}-- `FLCR-11` through `FLCR-18` for window, receipt, admission, CA, algebraic,\\
  curvature, residue, and exceptional machinery.
\noindent{}-- `FLCR-28` through `FLCR-30` for CAM/crystal, corpus ribbon, and universal\\
  normal-form intake.
\noindent{}-- `FLCR-31` through `FLCR-40` only after the LCR-native result has been cited\\
  and the translation claim has its own evidence lane.

\subsection*{9. Limitations And Falsifiers}

\noindent{}-- material-specific bands, lifetimes, mobilities, and spectra require data-bound calibration\\
\noindent{}-- External calibration claims require units, datasets, citations, and reproducible data binding.\\
\noindent{}-- A later translation paper may strengthen this result only by adding the missing lane evidence.\\

A falsifier for this paper is any example that satisfies the declared input
conditions while violating the stated construction, receipt, or lane boundary.
An interpretation that merely wants a stronger downstream conclusion is not a
falsifier; it is an obligation routed to a later paper.

\subsection*{10. Publication Readiness Tasks}

\noindent{}-- Validator identities and receipt hashes are recorded in the manifest or receipt appendix.\\
\noindent{}-- External theorems require final citation entries before journal submission.\\
\noindent{}-- Every theorem, proposition, and protocol must retain a claim lane and evidence boundary.\\
\noindent{}-- The Markdown, LaTeX, and PDF forms are generated from the same canonical source.\\

\subsection*{Dual Positioning: Story And Formal Carrier}

This paper must be read in two synchronized ways. Sequentially, it explains why
the next state exists in the corpus story. Formally, it binds that state to
accepted mathematics, IRL formalism, code receipts, validators, CAM/crystal
lookups, and claim-lane boundaries.

Assigned original ribbon role(s): orbital publication overlay.

\noindent\texttt{| Original slot | Family | Lift | Role | Proof form |}\\
\noindent\texttt{|---|---|---:|---|---|}\\
\noindent\texttt{| orbital | publication overlay | n/a | no legacy original slot assigned yet | intake and routing proof |}\\

The formal obligation is to state the strongest valid claim available for this
paper without letting interpretation silently change the addressed object. Any
author interpretation belongs beside the formalism as a declared relabeling,
bridge, or analog, and must be accompanied by the evidence lane that makes the
claim consumable by later papers.

\subsection*{State-Bound Proof Contract}

This paper receives: mature LCR-native corpus and orbital evidence intake.

It must produce: Electron-Hole-Exciton Accounting as publication overlay or synthesis route.

Semantic transition: route external, comparative, or synthesis material around the original proof ribbon without overwriting original slot obligations.

Accepted formalism targets to bind in the journal rewrite:

\noindent{}-- source routing and dependency graphs\\
\noindent{}-- citation-bound comparison\\
\noindent{}-- normal-form correspondence tables\\
\noindent{}-- falsifier and calibration boundaries\\

\noindent\texttt{| Slot | Contract |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| orbital | publication overlay; must declare sources, dependencies, and calibration/falsifier boundaries |}\\

The formal carrier uses these accepted tools while preserving interpretive
claims as explicit relabelings, correspondences, or bridges. Claim promotion is admissible only when a receipt, standard citation,
CAM/crystal reapplication, normal-form result, calibration datum, or falsifier
boundary is attached.

\subsection*{Provenance And Crystal Evidence Integration}

This section integrates prior work, CAM/crystal projections, NSIT tooling,
standards-window evidence, and routed supplements as provenance-bearing
evidence. Source material is not treated as manuscript text; it is bound into
the paper only through claim lanes, receipts, validators, normal forms,
calibration rows, or explicit falsifier boundaries.

\subsubsection*{Expansion Rule For This Slot}

Use past work as orbital evidence: route all imports through dependency, citation, normal-form, calibration, and falsifier lanes.

\subsubsection*{Primary Evidence Inputs}

\noindent\texttt{| Source | Placement reason |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| `NP-12\_Electron\_Hole\_Exciton\_Accounting\_For\_Open\_Math.md` | primary assigned source for the paper's formal spine |}\\
\noindent\texttt{| `supplements/SM\_BRIDGE\_SUPPLEMENT.md` | primary assigned source for the paper's formal spine |}\\

\subsubsection*{Secondary And Orbital Evidence Inputs}

\noindent\texttt{| Source | Placement reason |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| `supplements/SM\_BRIDGE\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/RECEIPT\_VERIFIER\_CATALOG.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/INTERNAL\_REASONING\_PYRAMID\_INDEX.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/INTERNAL\_REASONING\_5P\_WINDOW\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/INTERNAL\_REASONING\_7P\_WINDOW\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/INTERNAL\_REASONING\_9P\_WINDOW\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `CAM\_CLAIM\_100\_SCORE\_AUDIT.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `NSIT\_TOOL\_CLOSURE\_MATRIX.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `NSIT\_REASONED\_CLOSURE\_PASS.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `ORBITAL\_DATA\_CROSS\_POPULATION\_AUDIT.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `AGENT\_CRYSTAL\_WORK\_HARVEST.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `PAPER\_REWORKS\_CRYSTAL\_PROJECTION.json` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| Additional source routes | Complete routing is maintained in the source-placement appendix |}\\

\subsubsection*{Crystal And Standards Evidence To Bind}

\noindent{}-- Paper Reworks crystal projection: 33 paper markdown files, 9 supplements, 5 queues, 6 lattice-forge unification artifacts, 140 faces, 140 vignettes, and 280 CAM nodes.\\
\noindent{}-- Standards-window intake: 192/192 corpus conformance verdicts PASS; 140/142 obligations have candidate routes; 2/4/8/16/32 window lattice is available for cross-paper reads.\\
\noindent{}-- Agent/crystal harvest: agent-generated memory, runtime standards starter, current runtime build, repo-harvest CAM, notebook-derived bundles, and downloaded crystal payloads are orbital evidence surfaces.\\
\noindent{}-- NSIT inventory baseline: 220 validators, 1786 receipt/data artifacts, 1137 formal-paper-like artifacts, 114 supplements, and 86 memory/CAM artifacts.\\

\subsubsection*{Paper-Specific CAM/Score Rows}

No direct `00-32` CAM score row is assigned; use this paper as an orbital or translation intake.

\subsubsection*{Paper-Specific NSIT Closure Rows}

No direct NSIT row matched the assigned legacy papers in the first-pass matrix; validator matching by object name remains a receipt-attachment requirement.

\subsubsection*{Source Integration Summary}

The legacy source and internal reasoning supplement are treated as source
evidence rather than manuscript prose. Their contributions enter this paper as
claim-lane entries, receipt or validator references, finite-domain statements,
and limitation boundaries. Speculative or cross-domain interpretations remain
separate from closed local results until an explicit adapter, citation,
normal-form derivation, calibration row, or falsifier is attached.
\subsection*{Claim Binding Queue}

This queue records the evidence discipline for claim strengthening. It separates claims that already have support from residues that remain in falsifier or open-obligation lanes.

\noindent\texttt{| Queue | Promote now | Bind next | Residue |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| Electron-Hole-Exciton Standard Accounting | Promote standard hole/exciton vocabulary and LCR vacancy/residue bookkeeping when SMD-10 is cited. | Bind material model, band structure, effective masses, screening, and par}\\

\subsubsection*{Binding Discipline}

Each queue item is represented as a delta:

\begin{verbatim}
local claim at paper time
-> attached later source/tool/receipt/theorem
-> revised representation
-> invariant boundary and remaining residue
\end{verbatim}

This preserves the sequential story while allowing later tools, crystals, and
standard formalisms to return through the proper lane.

\subsection*{Claim Delta Ledger}

This ledger applies the paper's claim-binding queues as explicit back-application
deltas. It keeps the sequential paper story intact while allowing later
receipts, standard formalisms, CAM/crystal routes, and validators to sharpen the
claim.

\noindent\texttt{| Delta | Local claim at paper time | Later evidence | Revised representation | Boundary kept |}\\
\noindent\texttt{|---|---|---|---|---|}\\
\noindent\texttt{| Search By Object Name | No direct reasoned-closure queue was assigned from the first queue map. | Search source routing, verifier catalog, CAM/crystal routes, and paper-local object names. | Create a specific binding q}\\

The revised representation records the strongest claim supported by the current evidence package. Promotion into theorem or proposition language occurs only when the named evidence is attached in the manifest or workbook replay.

\subsection*{Source-Backed Evidence Summary}

Routed archive and mirror cards are treated as provenance summaries rather than
body text. They identify candidate receipts, validators, theorem registries, or
supplemental source routes. A card strengthens this paper only when its
contribution is bound to a claim lane, evidence object, and boundary.

\noindent\texttt{| Evidence card | Score | Publication contribution | Boundary |}\\
\noindent\texttt{|---|---:|---|---|}\\
\noindent\texttt{| No routed archive card attached yet | 0 | source-backed contribution | Source-backed support; promotion requires the paper-local claim lane and evidence boundary. |}\\
\noindent\texttt{| Additional evidence cards | 0 total | The complete card inventory is maintained in the archive evidence matrix. | Cards are source-discovery aids until bound to paper-local evidence. |}\\

\subsection*{Journal Apparatus}

\subsubsection*{Article Type And Intended Venue Fit}

This manuscript is written as a formal-methods and mathematical-systems paper
inside the series *Formalizing LCR, Unifying Standard Models*. Its intended
reader is a technical reviewer who needs claim boundaries, reproducibility
routes, and cross-paper dependencies to be visible without relying on private
context.

\subsubsection*{Structured Contribution Statement}

\noindent\texttt{| Item | Statement |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| Publication ID | `FLCR-34` |}\\
\noindent\texttt{| Legacy source slot(s) | `orbital` |}\\
\noindent\texttt{| Ribbon role | routes external, standard-model, or synthesis material around the original proof ribbon |}\\
\noindent\texttt{| Proof form | source intake, correspondence table, dependency statement, and falsifier boundary |}\\
\noindent\texttt{| Received state | mature LCR-native corpus and orbital evidence intake |}\\
\noindent\texttt{| Produced state | Electron-Hole-Exciton Accounting as publication overlay or synthesis route |}\\

\subsubsection*{Claim-Evidence Table}

\noindent\texttt{| Claim | Lane | Evidence to attach | Boundary |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| Theorem 34.1 | `standard\_theorem\_citation\_bound\_result` | Receipt, source card, validator, citation, or CAM route named in the paper manifest | standard electron, hole, recombination, screening, and exciton models can }\\
\noindent\texttt{| Proposition 34.2 | `normal\_form\_result` | Receipt, source card, validator, citation, or CAM route named in the paper manifest | exciton accounting can be imported by later papers only through its declared source, recei}\\
\noindent\texttt{| Protocol 34.3 | `falsifier\_or\_open\_obligation` | Receipt, source card, validator, citation, or CAM route named in the paper manifest | material-specific bands, lifetimes, mobilities, and spectra require data-bound cali}\\

\subsubsection*{Figure Plan}

\noindent\texttt{| Figure | Purpose | Caption |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| FLCR-34-F1 | Publication overlay dependency map | Schematic showing how `FLCR-34` turns its received state into the produced state while preserving claim lanes and residue boundaries. |}\\
\noindent\texttt{| FLCR-34-F2 | Evidence routing map | Diagram of source papers, archive cards, CAM/crystal routes, validators, and workbook replay paths used by this manuscript. |}\\
\noindent\texttt{| FLCR-34-F3 | Same-family lift context | Diagram placing this paper in the original `00-79` ribbon family and showing predecessor/successor slots. |}\\

\subsubsection*{In-Text Figure FLCR-34-F1: Publication overlay dependency map}

\begin{verbatim}
received state
  -> Publication overlay dependency map
  -> formal claim lane
  -> evidence object / receipt / citation
  -> produced state
  -> remaining residue
\end{verbatim}

\subsubsection*{Table Plan}

\noindent\texttt{| Table | Purpose |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| FLCR-34-T1 | Dependency and translation table |}\\
\noindent\texttt{| FLCR-34-T2 | Claim-lane/evidence-boundary table |}\\
\noindent\texttt{| FLCR-34-T3 | Archive evidence card and source-backed upgrade table |}\\
\noindent\texttt{| FLCR-34-T4 | Workbook replay and falsifier table |}\\

\subsubsection*{Worked Example}

Route one standard-model or synthesis claim back to its LCR-native source papers. The example must name the input object, the operation,
the evidence object, the allowed revised claim, and the remaining boundary.

\subsubsection*{Nomenclature And Glossary}

\noindent\texttt{| Term | Paper-local meaning |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| CAM | Defined by this paper as part of the `publication\_overlay` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| claim lane | Defined by this paper as part of the `publication\_overlay` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| crystal | Defined by this paper as part of the `publication\_overlay` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| dependency | Defined by this paper as part of the `publication\_overlay` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| publication overlay | Defined by this paper as part of the `publication\_overlay` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| receipt | Defined by this paper as part of the `publication\_overlay` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| synthesis lane | Defined by this paper as part of the `publication\_overlay` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| translation claim | Defined by this paper as part of the `publication\_overlay` proof role; final definition is recorded in the paper-local glossary. |}\\

\subsubsection*{Appendix FLCR-34-A: Evidence Package}

The appendix records:

1. Legacy source excerpts or source-card references used in the final claim ledger.
2. Receipt and verifier paths, including pass/fail/partial status.
3. CAM/crystal query or projection rows used by the paper, with source identity and boundary.
4. Standards-window and NSIT evidence used for conformance or routing.
5. Falsifier, calibration, or external-data rows that remain unresolved.

\subsubsection*{Data And Code Availability}

The publication package contains the canonical Markdown sources, manifests, source-routing matrices, validation reports, and generated PDF/TeX outputs.

Code and verifier references are cited through manifests, archive evidence cards, receipt catalogs, or workbook replay tables. External datasets or
standards citations must be attached before any calibration-bound claim is
promoted.

\subsubsection*{Reviewer Checklist}

\noindent\texttt{| Check | Reviewer question |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| Claim lane | Does every strong claim declare its lane and evidence type? |}\\
\noindent\texttt{| Boundary | Does the paper preserve what it does not prove? |}\\
\noindent\texttt{| Reproducibility | Is there a receipt, verifier, source card, citation, or replay table for the claim? |}\\
\noindent\texttt{| Cross-paper import | Does the paper cite the prior FLCR/OPR slot before consuming its result? |}\\
\noindent\texttt{| Interpretation | Does the analog layer preserve the addressed state while changing labels/access paths? |}\\

\subsubsection*{Declarations}

No human-subjects, clinical, or animal-research protocol is asserted by this
paper. External empirical claims require separate dataset, calibration, or
domain-validation attachments. Competing-interest and funding statements are recorded in the submission metadata.

\subsection*{11. Publication Integration Addendum}

\subsubsection*{11.1 Role In The Series}

`FLCR-34` (`Electron-Hole-Exciton Accounting`) occupies the `publication\_overlay` role at lift depth `n/a`.
The paper receives mature LCR-native corpus and orbital evidence intake. It produces Electron-Hole-Exciton Accounting as publication overlay or synthesis route. The state transition is:
route external, comparative, or synthesis material around the original proof ribbon without overwriting original slot obligations.

The paper-local proof form is:

\begin{verbatim}
source intake, correspondence table, dependency statement, and falsifier boundary
\end{verbatim}

The integration result is a source-intake and synthesis surface with dependency, citation, calibration, and falsifier boundaries. This addendum records how that result is
consumed by the publication series without relying on editorial instructions or
private working context.

\subsubsection*{11.2 Formal Carrier}

\noindent\texttt{| Formal carrier | Function |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| source routing and dependency graphs | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| citation-bound comparison | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| normal-form correspondence tables | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| falsifier and calibration boundaries | Formal carrier for the paper-local result. |}\\

The LCR, CAM, crystal, forge, and analog vocabulary functions as a typed access
layer over these carriers. A relabeling is admissible only when the addressed
object, evidence lane, boundary, and downstream import rule remain attached.

\subsubsection*{11.3 Claim Ledger}

\noindent\texttt{| Claim | Lane | Statement |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| Theorem 34.1 | `standard\_theorem\_citation\_bound\_result` | standard electron, hole, recombination, screening, and exciton models can explain part of the open residue surface when material context is declared |}\\
\noindent\texttt{| Proposition 34.2 | `normal\_form\_result` | exciton accounting can be imported by later papers only through its declared source, receipt, and lane. |}\\
\noindent\texttt{| Protocol 34.3 | `falsifier\_or\_open\_obligation` | material-specific bands, lifetimes, mobilities, and spectra require data-bound calibration |}\\

These claims are consumed at their stated lane. A stronger downstream statement
creates a new claim envelope with its own evidence object.

\subsubsection*{11.4 Evidence Package}

\noindent\texttt{| Evidence class | Routed items | Status |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| Legacy sources | `NP-12\_Electron\_Hole\_Exciton\_Accounting\_For\_Open\_Math.md`, `supplements/SM\_BRIDGE\_SUPPLEMENT.md` | routed evidence |}\\
\noindent\texttt{| Evidence inputs | `CAM\_CLAIM\_100\_SCORE\_AUDIT.md`, `NSIT\_TOOL\_CLOSURE\_MATRIX.md`, `NSIT\_REASONED\_CLOSURE\_PASS.md`, `PAPER\_REWORKS\_CRYSTAL\_PROJECTION.json` | routed evidence |}\\
\noindent\texttt{| CAM/crystal sources | `PAPER\_REWORKS\_CRYSTAL\_PROJECTION.json`, `AGENT\_CRYSTAL\_WORK\_HARVEST.json`, `runtime standards artifact`, `notebook-derived source bundle` | routed evidence |}\\
\noindent\texttt{| Standards-window inputs | `window\_summary.json`, `node DBs`, `window DBs` | routed evidence |}\\
\noindent\texttt{| Receipts | external requirement | not attached in this source package |}\\
\noindent\texttt{| Validators | external requirement | not attached in this source package |}\\

Standards-window, runtime, and notebook-derived artifacts are treated
as evidence-routing surfaces. They support source discovery, conformance
checking, and reapplication, but they do not replace citations, receipts,
normal-form derivations, calibration rows, or falsifiers.

\subsubsection*{11.5 Results Representation}

The paper's results section is organized around five publication objects:

1. the exact object acted on at this slot;
2. the admissible operation or transformation;
3. the receipt, enumeration, derivation, lookup, or external theorem supporting
   the operation;
4. the residue or boundary left after the result;
5. the downstream import rule.

\subsubsection*{11.6 Figures And Tables}

\noindent\texttt{| Figure | Role |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| FLCR-34-F1: Publication overlay dependency map | Visualizes the proof object, routing, or boundary. |}\\
\noindent\texttt{| FLCR-34-F2: Evidence routing map | Visualizes the proof object, routing, or boundary. |}\\
\noindent\texttt{| FLCR-34-F3: Same-family lift context | Visualizes the proof object, routing, or boundary. |}\\

\noindent\texttt{| Table | Role |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| FLCR-34-T1: Dependency and translation table | Records claim lanes, evidence, sources, or falsifiers. |}\\
\noindent\texttt{| FLCR-34-T2: Claim-lane/evidence-boundary table | Records claim lanes, evidence, sources, or falsifiers. |}\\
\noindent\texttt{| FLCR-34-T3: Archive evidence card and source-backed upgrade table | Records claim lanes, evidence, sources, or falsifiers. |}\\
\noindent\texttt{| FLCR-34-T4: Workbook replay and falsifier table | Records claim lanes, evidence, sources, or falsifiers. |}\\

\subsubsection*{11.7 Limits And Falsifiers}

The paper proves only the object and domain declared in its claim ledger.
Physical, Standard Model, observer, calibration, or synthesis claims require
the additional lane evidence stated by their destination papers. CAM/crystal
and forge language is operational only when represented as an address, lookup,
receipt, validator, or reapplication path.
\end{document}
