\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{longtable}
\usepackage{array}
\begin{document}
﻿\# FLCR-35 - GR, Curvature, And Continuum Translation

**Series:** Formalizing LCR, Unifying Standard Models
**Artifact:** formal paper source
**Status:** first-pass rich rewrite; requires final citation and build pass.
**Claim posture:** maximal local claim posture with explicit lane boundaries.

\subsection*{Abstract}

This paper formalizes general-relativity and continuum language as translation of repair-curvature and edge residuals. The operative object is GR-continuum translation. The core result is that discrete repair-curvature and continuum-edge rows can be translated into GR-facing claims only when metric, limit, and calibration assumptions are explicit. The paper also defines how this result routes forward: FLCR-35 cites FLCR-15 and FLCR-17 as its LCR-native base. Its main residue is explicit: Einstein-field-equation identity and measured spacetime curvature remain external calibration.

\subsection*{Keywords}

GR-continuum translation; LCR; receipt; claim lane; normal form.

\subsection*{External Reader Orientation}

An outside reviewer should read this paper as a translation and comparator paper. Its local object is **GR, Curvature, And Continuum Translation**. The paper's immediate contribution is: Translates GR/continuum language through repair and sampling gates.

The nearest external anchors are standard mathematical physics definitions, cited Standard Model targets, calibrated constants or data where available, and the LCR-native papers that provide the source-side object. LCR terms are therefore internal labels for the construction unless a row explicitly imports an external theorem, citation, dataset, or calibration target.

It may close the external target definition and the internal translation grammar, but it does not claim measured physical identity unless a calibration/comparator row is present.

\subsection*{Reviewer Compression}

**Core object.** GR, Curvature, And Continuum Translation.

**Primary result.** This paper contributes a controlled mapping between a cited external target and a cited LCR-native source object.

**Primary non-result.** This paper does not claim measured physical identity unless the comparator/calibration row is attached.

**Review strategy.** Evaluate the formal claim rows first, then inspect the receipt/citation/calibration rows that support each claim. Appendices provide routing and implementation context; they should not be read as stronger than their lane permits.

\subsection*{Peer Reviewer Assessment}

Reviewer assumption: the reviewer has been briefed on the FLCR structure, claim lanes, CAM/crystal routing, forge/action surfaces, and the distinction between internal formal results and external physical calibration.

**Recommendation.** major revision, technically promising.

**Review score vector.** orientation=2, claim\_granularity=2, evidence\_visibility=2, falsifier\_visibility=2, journal\_apparatus=1, external\_target\_boundary=2.

**Formal claim rows reviewed.** 3.

\subsubsection*{Reviewer Strength Finding}

The manuscript correctly treats Standard Model language as an external target surface and keeps translation claims separate from measured physical identity.

\subsubsection*{Major Revision Requests}

\noindent{}-- Convert the strongest proof sketch into numbered definitions, lemmas, and propositions with explicit dependencies.\\
\noindent{}-- Replace placeholder source classes with final citation keys, receipt hashes, or dataset identifiers wherever possible.\\
\noindent{}-- Move repeated pass-derived material into a compact evidence appendix and keep the main body focused on the paper-local argument.\\
\noindent{}-- Add a comparator table mapping each external target object to the exact LCR source object, invariant, calibration status, and falsifier.\\

\subsubsection*{Minor Revision Requests}

\noindent{}-- Normalize theorem capitalization and punctuation.\\
\noindent{}-- Add final figure/table captions where the text currently describes diagrams schematically.\\
\noindent{}-- Ensure every acronym and local term appears in the paper-local glossary.\\
\noindent{}-- State scale, scheme, and units for any physics-facing numerical comparator.\\

\subsubsection*{Acceptance Blockers}

\noindent{}-- Measured physical identity cannot be accepted without comparator/calibration rows.\\
\noindent{}-- The mapping from external target to LCR source must be explicit enough that another reviewer could reject or reproduce it.\\


\subsection*{1. Contribution And Scope}

\noindent{}-- Defines GR-continuum translation as a first-class FLCR object.\\
\noindent{}-- States the local result: discrete repair-curvature and continuum-edge rows can be translated into GR-facing claims only when metric, limit, and calibration assumptions are explicit.\\
\noindent{}-- Routes downstream use through claim lanes rather than inherited prose: FLCR-35 cites FLCR-15 and FLCR-17 as its LCR-native base.\\
\noindent{}-- Preserves the residue boundary: Einstein-field-equation identity and measured spacetime curvature remain external calibration.\\

This paper belongs to the Standard Model translation band. Standard Model language names an external target surface, not an automatic LCR identity. A translation claim is admissible only when the cited standard object, the LCR-native source object, the mapping rule, the evidence lane, and the falsifier or calibration boundary are all visible.

\subsection*{2. Source Routing}

Primary routed sources:

\noindent{}-- `14\_GR\_Boundary\_Repair\_Curvature.md`\\
\noindent{}-- `16\_Continuum\_Edge\_Residuals.md`\\
\noindent{}-- `supplements/SM\_BRIDGE\_SUPPLEMENT.md`\\

Cross-corpus evidence classes:

\noindent{}-- `CAM\_CLAIM\_100\_SCORE\_AUDIT.md`\\
\noindent{}-- `NSIT\_TOOL\_CLOSURE\_MATRIX.md`\\
\noindent{}-- `NSIT\_REASONED\_CLOSURE\_PASS.md`\\
\noindent{}-- `PAPER\_REWORKS\_CRYSTAL\_PROJECTION.json`\\
\noindent{}-- standards, glue, window, and node databases where applicable\\
\noindent{}-- notebook-derived review prompts and orbital source manifests\\

\subsection*{3. Definitions}

\noindent{}-- **Metric assumption.** The added structure needed before repair rows become metric data.\\
\noindent{}-- **Continuum limit.** A limiting operation with declared topology, norm, and convergence claim.\\
\noindent{}-- **Receipt boundary.** The exact scope in which the paper's result can be replayed or consumed.\\
\noindent{}-- **Promotion route.** The evidence path required before a stronger downstream claim can use this result.\\

\subsection*{4. Formal Claims}

\noindent\texttt{| Claim | Lane | Statement |}\\
\noindent\texttt{|-------|------|-----------|}\\
\noindent\texttt{| Theorem 35.1 | `external\_calibration\_result` | discrete repair-curvature and continuum-edge rows can be translated into GR-facing claims only when metric, limit, and calibration assumptions are explicit |}\\
\noindent\texttt{| Proposition 35.2 | `normal\_form\_result` | GR-continuum translation can be imported by later papers only through its declared source, receipt, and lane. |}\\
\noindent\texttt{| Protocol 35.3 | `falsifier\_or\_open\_obligation` | Einstein-field-equation identity and measured spacetime curvature remain external calibration |}\\

\subsection*{Reviewer Claim Ledger}

This ledger expands the formal-claims table into review actions. It is intended to make proof granularity explicit: what is being claimed, what evidence type can support it, what boundary remains, and what the next review action is.

\noindent\texttt{| Formal row | Type | Claim in review terms | Evidence required | Boundary | Next review action |}\\
\noindent\texttt{|---|---|---|---|---|---|}\\
\noindent\texttt{| Theorem 35.1 | external target or comparator | discrete repair-curvature and continuum-edge rows can be translated into GR-facing claims only when metric, limit, and calibration assumptions are explicit | dataset, meas}\\
\noindent\texttt{| Proposition 35.2 | translation grammar | GR-continuum translation can be imported by later papers only through its declared source, receipt, and lane | definitions, normal-form construction, conversion rule, and downst}\\
\noindent\texttt{| Protocol 35.3 | obligation/falsifier | Einstein-field-equation identity and measured spacetime curvature remain external calibration | explicit missing derivation, adapter, receipt, dataset, comparator, or failed test }\\

\subsection*{Claim Granularity And Review Table}

The table below separates the claim types so the paper is reviewable without accepting the whole FLCR vocabulary at once.

\noindent\texttt{| Claim type | What this paper may claim | Acceptance test | What is not claimed by that row |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| Formal-system result | `FLCR-35` defines or uses **GR, Curvature, And Continuum Translation** as a typed FLCR object with declared inputs, operations, outputs, and residue. | Definitions, formal claims, construction st}\\
\noindent\texttt{| Computational or receipt-bound result | Enumerations, TarPit runs, CAM/crystal routes, verifier rows, and generated artifacts are claims about the stated finite or executable domain. | A named receipt, validator, manif}\\
\noindent\texttt{| Imported theorem or external definition | The Standard Model or adjacent physics object is closed only as an external target definition when the relevant definition/citation row is present. | The source theorem, defini}\\
\noindent\texttt{| Interpretive bridge or analogy | Analog, workbook, visual, or translation language may explain why the construction is useful. | The analogy preserves the relevant structure and does not promote itself into a theorem. }\\
\noindent\texttt{| Physical or calibration-facing claim | Measured values, physical identity, and predictive accuracy require scale, units, dataset, uncertainty, comparator, and pass/fail criteria. | A dataset, citation, calibration prot}\\
\noindent\texttt{| Open obligation or falsifier | A missing derivation, adapter, receipt, dataset, or failed comparator is a named research channel. | The next binding action and the reason the stronger claim is not closed are stated. | }\\

\subsection*{5. Paper-Specific Development}

1. Identify the local object and its assigned sources for FLCR-35.
2. Separate what is internally receipt-bound from what is citation-bound, CAM-bound, calibration-bound, or still an obligation.
3. State the strongest admissible claim in its current lane.
4. Export only the lane-safe result to downstream papers and preserve the residue.

\subsubsection*{Proof Sketch}

The proof strategy for FLCR-35 is a typed construction argument. The paper names metric assumption as the active object, binds it to the routed legacy and orbital sources, and then allows downstream use only through the declared claim lane. This does not erase stronger ambitions; it keeps them addressable as dependencies, calibration tasks, or falsifiers.

\subsection*{6. Construction}

The construction is intentionally staged. First, the paper names the finite or
typed object that can be inspected directly. Second, it declares the admissible
operations over that object. Third, it records the receipt or source class that
allows another paper to consume the result. Fourth, it names the residue that
must not be silently promoted.

For this paper, the operative object is `GR, Curvature, And Continuum Translation`. Its safe consumption
rule is:

\begin{verbatim}
source object -> declared operation -> receipt/lane -> downstream import
\end{verbatim}

The unsafe consumption rule is:

\begin{verbatim}
source phrase -> downstream identity claim
\end{verbatim}

That second pattern is explicitly rejected by FLCR-01 and must be rewritten as
a claim-lane promotion with evidence.

\subsection*{7. Evidence And Receipts}

\noindent\texttt{| Evidence source | What it contributes |}\\
\noindent\texttt{|-----------------|---------------------|}\\
\noindent\texttt{| Legacy paper body | Primary formal and source-integration material assigned by the series map. |}\\
\noindent\texttt{| Internal and pyramid supplements | Cross-paper reasoning windows, deferred back-application slots, and route constraints. |}\\
\noindent\texttt{| NSIT tool closure matrix | Existing verifier/tool families that can close internal or batch claims. |}\\
\noindent\texttt{| CAM/crystal and standards-window evidence | Projected memory, source routing, standards reports, and window/node databases. |}\\

\subsubsection*{Standard Model Definition Dependencies}

This paper consumes the dedicated Standard Model Defining layer. These papers define the external Standard Model or adjacent standard-physics object before this FLCR paper translates it into LCR language.

\noindent\texttt{| SMD paper | Definition surface | Required use |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| `SMD-01` | Standard Model Definition Contract And Evidence Boundary | Definition surface that must be cited before this paper promotes the corresponding Standard Model-facing claim. |}\\
\noindent\texttt{| `SMD-02` | Gauge Principle, Connections, And Local Symmetry | Definition surface that must be cited before this paper promotes the corresponding Standard Model-facing claim. |}\\
\noindent\texttt{| `SMD-11` | GR Continuum Interface And Units-Bearing Calibration | Definition surface that must be cited before this paper promotes the corresponding Standard Model-facing claim. |}\\
\noindent\texttt{| `SMD-12` | Standard Model Comparator And Falsifier Protocol | Definition surface that must be cited before this paper promotes the corresponding Standard Model-facing claim. |}\\

This paper also imports SMB-01, the Standard Model Closure Bridge. SMB-01 supplies the closure-by-lane rule: rows are no longer treated as unresolved by default; they are closed when standard formalism, FLCR proof, CAM/crystal reapplication, normal-form translation, or external calibration satisfies the lane, and they remain obligations only when a required field is missing.

\subsubsection*{Closed Rows Applied In This Paper}

\noindent\texttt{| Row | Closure | Evidence | Boundary |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| Continuum/GR interface requirements | closed as boundary protocol | `SMD-11`, CODATA/NIST source registry | Closes what must be present for a physical continuum claim. |}\\
\noindent\texttt{| LCR boundary-repair curvature | closed internally at repair-ledger scope | `FLCR-15`, `FLCR-17` | Closes repair-demand curvature as internal accounting. |}\\
\noindent\texttt{| Physical GR identity | not closed here | `SMD-11` | Requires metric, stress-energy, units, and calibration. |}\\

The paper can now stop treating curvature language as wholly unresolved. The internal repair-curvature row is closed at its own scope. The external GR row is known as standard formalism. What remains open is the bridge that would identify or calibrate one as the other.

\subsubsection*{Active Comparator Rows}

\noindent\texttt{| Comparator | External side | LCR side | Current result | Next required action |}\\
\noindent\texttt{|---|---|---|---|---|}\\
\noindent\texttt{| Curvature definition | metric/connection/curvature tensor | boundary repair score/ledger | domains separated | Add mapping only if tensor/limit rule is stated. |}\\
\noindent\texttt{| Continuum limit | sampling/limit/norm | discrete LCR windows | protocol closed | Provide convergence or counterexample policy. |}\\
\noindent\texttt{| Units-bearing physics | CODATA/NIST constants and dimensions | unitless internal residue unless calibrated | calibration-bound | Add units and measured dataset before physical claim. |}\\

\subsubsection*{Executable Evidence Bound In This Pass}

This paper now binds continuum and curvature claims to the existing repair-ledger and edge-residual verifier routes. The paper therefore separates structural curvature from physical GR curvature instead of leaving the distinction implicit.

\noindent\texttt{| Evidence | Path | Result imported here | Boundary preserved |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| Continuum/GR definition surface | `SMD-11` | Closes the rule that continuum and curvature translations require sampling/limit rule plus units-bearing calibration before physical identity is claimed. | No GR identity fo}\\
\noindent\texttt{| Boundary-repair curvature verifier route | `local evidence artifact` | Catalogs `python production/formal-papers/CQE-paper-14/verify\_boundary\_repair\_curvature.py`; verifier checks typed transport obligations, proof-bou}\\
\noindent\texttt{| Continuum edge residual verifier route | `local evidence artifact` | Catalogs `python production/formal-papers/CQE-paper-16/verify\_continuum\_edge\_residuals.py`; verifier checks at-most-three S3 anneal closure, four Lie}\\

The upgraded claim is: FLCR-35 may state structural curvature as repair demand when the repair-ledger route is cited. Physical GR claims must still supply metric, stress-energy, units, limit/sampling rule, dataset, and pass/fail comparator.

\subsubsection*{Online Source Rows Applied In This Pass}

\noindent\texttt{| Online source | Claim-lane effect | Boundary retained |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| `IRL-LRR-GR-HYPERBOLIC` | Supplies a GR/continuum formalism reference for Einstein-equation PDE/hyperbolic treatment after gauge and constraint handling. | Does not identify discrete repair curvature with physical spac}\\
\noindent\texttt{| `IRL-CODATA-2022-WALLET` | Supplies constants/unit rows for any gravity or continuum calibration claim. | Units and constants do not close the limit map. |}\\

Online data therefore closes the source-availability problem for GR/continuum framing. FLCR-35 still needs an explicit sampling/limit map and units-bearing comparator before physical identity is promoted.

\subsubsection*{Assertive Closure Promotions}

\noindent\texttt{| Row | Closure now allowed | Evidence | Residue moved out of the open row |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| GR/continuum external formalism | closed by citation | `IRL-LRR-GR-HYPERBOLIC`, `SMD-11` | Physical identity with discrete repair curvature. |}\\
\noindent\texttt{| Structural repair curvature | closed internally when verifier route/receipt is cited | repair-curvature verifier route, edge-residual route, FLCR repair papers | Continuum limit and units-bearing calibration. |}\\
\noindent\texttt{| Unit/calibration target | closed as source-available | NIST/CODATA | Derivation or measured GR comparison. |}\\

The non-timid conclusion is: FLCR-35 can close the external formalism and internal structural-curvature lane. The remaining open work is the explicit limit/calibration bridge.

\subsection*{Appendix D. Resolved-State Closure Pass}

This pass removes false restrictions on the paper's claim posture. A row is no longer called open merely because a stronger future claim exists. The satisfied lane is closed now; only the stronger claim that lacks its required adapter, comparator, calibration, or falsifier remains as residue.

\subsubsection*{Closed Now}

\noindent\texttt{| Row | Lane | Resolved state | Remaining boundary |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| paper lift enumeration | `receipt\_bound\_internal\_result` | 8/8 LCR states succeeded; error walls=0; avg TarPit mass=0.514152. | This closes the paper-local finite lift readout, not every stronger physical interpretatio}\\
\noindent\texttt{| boundary repair | `normal\_form\_result` | The typed boundary repair surface is closed as an admission table for legal next-state repair. | The family closure is a structural lane; measured physics still requires destina}\\
\noindent\texttt{| decade-4 tower | `receipt\_bound\_internal\_result` | The decade tower is resolved with avg TarPit mass=0.509077 and mass sum=40.726174. | The decade total is an internal tower metric, not a standalone universal physical }\\
\noindent\texttt{| family-05 cross-lift comparison | `cam\_crystal\_reapplication\_result` | Family tower binds FLCR-05, FLCR-15, FLCR-25, FLCR-35; avg TarPit mass=0.514757; error walls=0. | Cross-lift agreement strengthens routing and comp}\\
\noindent\texttt{| GR/continuum interface | `standard\_theorem\_citation\_bound\_result` | GR/continuum source availability and boundary protocol are closed. | Discrete-to-GR physical identity requires limit/calibration proof. |}\\

\subsubsection*{Claim Posture After This Pass}

`FLCR-35` should now be read as a resolved-state contribution for `GR, Curvature, And Continuum Translation` at its declared lane. The paper may state the strongest claim supported by these rows directly. It should reserve caution only for a specifically named stronger claim whose required evidence is absent.

\subsection*{8. Dependencies And Downstream Use}

This paper may be imported by later FLCR papers only through the claim lanes
above. The default downstream consumers are:

\noindent{}-- `FLCR-11` through `FLCR-18` for window, receipt, admission, CA, algebraic,\\
  curvature, residue, and exceptional machinery.
\noindent{}-- `FLCR-28` through `FLCR-30` for CAM/crystal, corpus ribbon, and universal\\
  normal-form intake.
\noindent{}-- `FLCR-31` through `FLCR-40` only after the LCR-native result has been cited\\
  and the translation claim has its own evidence lane.

\subsection*{9. Limitations And Falsifiers}

\noindent{}-- Einstein-field-equation identity and measured spacetime curvature remain external calibration\\
\noindent{}-- External calibration claims require units, datasets, citations, and reproducible data binding.\\
\noindent{}-- A later translation paper may strengthen this result only by adding the missing lane evidence.\\

A falsifier for this paper is any example that satisfies the declared input
conditions while violating the stated construction, receipt, or lane boundary.
An interpretation that merely wants a stronger downstream conclusion is not a
falsifier; it is an obligation routed to a later paper.

\subsection*{10. Publication Readiness Tasks}

\noindent{}-- Validator identities and receipt hashes are recorded in the manifest or receipt appendix.\\
\noindent{}-- External theorems require final citation entries before journal submission.\\
\noindent{}-- Every theorem, proposition, and protocol must retain a claim lane and evidence boundary.\\
\noindent{}-- The Markdown, LaTeX, and PDF forms are generated from the same canonical source.\\

\subsection*{Dual Positioning: Story And Formal Carrier}

This paper must be read in two synchronized ways. Sequentially, it explains why
the next state exists in the corpus story. Formally, it binds that state to
accepted mathematics, IRL formalism, code receipts, validators, CAM/crystal
lookups, and claim-lane boundaries.

Assigned original ribbon role(s): `14`/boundary\_action, `16`/ledger\_action.

\noindent\texttt{| Original slot | Family | Lift | Role | Proof form |}\\
\noindent\texttt{|---|---|---:|---|---|}\\
\noindent\texttt{| `14` | boundary\_action | 1 | order-2 slot-4: type the boundary, repair row, or curvature-demand condition | typed boundary row and next-state admissibility |}\\
\noindent\texttt{| `16` | ledger\_action | 1 | order-2 slot-6: bind state into causal, observer, or synchronization ledgers | ledger, graph, and synchronization proof |}\\

The formal obligation is to state the strongest valid claim available for this
paper without letting interpretation silently change the addressed object. Any
author interpretation belongs beside the formalism as a declared relabeling,
bridge, or analog, and must be accompanied by the evidence lane that makes the
claim consumable by later papers.

\subsection*{State-Bound Proof Contract}

This paper receives: state emitted by prior slot 13 and reopened at original slot 14 (GR Boundary Repair Curvature).

It must produce: formal result of original slot 16 plus the same-family lift path toward slot 26.

Semantic transition: type the boundary condition that decides whether the state repairs, reflects, curves, or routes onward; bind state changes into causal, observer, synchronization, or obligation ledgers.

Accepted formalism targets to bind in the journal rewrite:

\noindent{}-- boundary value problems\\
\noindent{}-- typed interfaces and admissibility conditions\\
\noindent{}-- topological boundary/interior distinction\\
\noindent{}-- falsifier rows for failed promotions\\
\noindent{}-- directed graphs and partial orders\\
\noindent{}-- causal/event ledgers\\
\noindent{}-- synchronization protocols\\
\noindent{}-- traceability and provenance invariants\\

\noindent\texttt{| Slot | Family | Lift | Produced proof form |}\\
\noindent\texttt{|---|---|---:|---|}\\
\noindent\texttt{| `14` | boundary\_action | 1 | typed boundary row and next-state admissibility |}\\
\noindent\texttt{| `16` | ledger\_action | 1 | ledger, graph, and synchronization proof |}\\

The formal carrier uses these accepted tools while preserving interpretive
claims as explicit relabelings, correspondences, or bridges. Claim promotion is admissible only when a receipt, standard citation,
CAM/crystal reapplication, normal-form result, calibration datum, or falsifier
boundary is attached.

\subsection*{Provenance And Crystal Evidence Integration}

This section integrates prior work, CAM/crystal projections, NSIT tooling,
standards-window evidence, and routed supplements as provenance-bearing
evidence. Source material is not treated as manuscript text; it is bound into
the paper only through claim lanes, receipts, validators, normal forms,
calibration rows, or explicit falsifier boundaries.

\subsubsection*{Expansion Rule For This Slot}

Use past work to type the boundary: admitted, repaired, reflected, calibration-required, falsified, or routed onward.

\subsubsection*{Primary Evidence Inputs}

\noindent\texttt{| Source | Placement reason |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| `14\_GR\_Boundary\_Repair\_Curvature.md` | primary assigned source for the paper's formal spine |}\\
\noindent\texttt{| `16\_Continuum\_Edge\_Residuals.md` | primary assigned source for the paper's formal spine |}\\
\noindent\texttt{| `supplements/14\_INTERNAL\_REASONING\_SUPPLEMENT.md` | paper-local reasoning supplement contributing to definitions, proof sketch, and limitations |}\\
\noindent\texttt{| `supplements/16\_INTERNAL\_REASONING\_SUPPLEMENT.md` | paper-local reasoning supplement contributing to definitions, proof sketch, and limitations |}\\
\noindent\texttt{| `virtuous\textbackslash{}14\_GR\_Boundary-Repair\_Curvature\_VIRTUOUS.md` | prior enriched paper body; should be mined for mature claims and proof ordering |}\\
\noindent\texttt{| `virtuous\textbackslash{}16\_Continuum\_Edge\_Residuals\_VIRTUOUS.md` | prior enriched paper body; should be mined for mature claims and proof ordering |}\\

\subsubsection*{Secondary And Orbital Evidence Inputs}

\noindent\texttt{| Source | Placement reason |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| `supplements/SM\_BRIDGE\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/RECEIPT\_VERIFIER\_CATALOG.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/INTERNAL\_REASONING\_PYRAMID\_INDEX.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/INTERNAL\_REASONING\_5P\_WINDOW\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/INTERNAL\_REASONING\_7P\_WINDOW\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `supplements/INTERNAL\_REASONING\_9P\_WINDOW\_SUPPLEMENT.md` | cross-cutting supplement; paper-relevant rows, receipts, and guard language are bound through evidence lanes |}\\
\noindent\texttt{| `CAM\_CLAIM\_100\_SCORE\_AUDIT.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `NSIT\_TOOL\_CLOSURE\_MATRIX.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `NSIT\_REASONED\_CLOSURE\_PASS.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `ORBITAL\_DATA\_CROSS\_POPULATION\_AUDIT.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `AGENT\_CRYSTAL\_WORK\_HARVEST.md` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| `PAPER\_REWORKS\_CRYSTAL\_PROJECTION.json` | series-wide audit/score/closure evidence; import paper-specific rows and leave global context outside the body |}\\
\noindent\texttt{| Additional source routes | Complete routing is maintained in the source-placement appendix |}\\

\subsubsection*{Crystal And Standards Evidence To Bind}

\noindent{}-- Paper Reworks crystal projection: 33 paper markdown files, 9 supplements, 5 queues, 6 lattice-forge unification artifacts, 140 faces, 140 vignettes, and 280 CAM nodes.\\
\noindent{}-- Standards-window intake: 192/192 corpus conformance verdicts PASS; 140/142 obligations have candidate routes; 2/4/8/16/32 window lattice is available for cross-paper reads.\\
\noindent{}-- Agent/crystal harvest: agent-generated memory, runtime standards starter, current runtime build, repo-harvest CAM, notebook-derived bundles, and downloaded crystal payloads are orbital evidence surfaces.\\
\noindent{}-- NSIT inventory baseline: 220 validators, 1786 receipt/data artifacts, 1137 formal-paper-like artifacts, 114 supplements, and 86 memory/CAM artifacts.\\

\subsubsection*{Paper-Specific CAM/Score Rows}

\noindent\texttt{| 14 | 87 | internal curvature map closed | CL affirmative verifier: curvature = correction = C-participation, Rule90 flat | measured GR/Einstein bridge and physical calibration |}\\
\noindent\texttt{| 16 | 79 | partial/system-closeable | continuum edge residuals, Paper 07 bridge, Paper 02 correction, power-of-ten windows | global continuum limit and McKay/O2-prime collapse |}\\

\subsubsection*{Paper-Specific NSIT Closure Rows}

No direct NSIT row matched the assigned legacy papers in the first-pass matrix; validator matching by object name remains a receipt-attachment requirement.

\subsubsection*{Source Integration Summary}

The legacy source and internal reasoning supplement are treated as source
evidence rather than manuscript prose. Their contributions enter this paper as
claim-lane entries, receipt or validator references, finite-domain statements,
and limitation boundaries. Speculative or cross-domain interpretations remain
separate from closed local results until an explicit adapter, citation,
normal-form derivation, calibration row, or falsifier is attached.
\subsection*{Claim Binding Queue}

This queue records the evidence discipline for claim strengthening. It separates claims that already have support from residues that remain in falsifier or open-obligation lanes.

\noindent\texttt{| Queue | Lane | Promote now | Bind next | Residue |}\\
\noindent\texttt{|---|---|---|---|---|}\\
\noindent\texttt{| Symbolic Carrier Versus Physical Carrier | `external\_calibration\_result` | Promote addressable symbolic-carrier and transport claims where the paper names carrier, path, residue, or traversal rules. | Map every physica}\\
\noindent\texttt{| Electron-Hole-Exciton Standard Accounting | `standard\_theorem\_citation\_bound\_result` | Treat hole, vacancy, exciton, recombination, screening, band-gap, and effective-mass language as standard-model correspondence when}\\
\noindent\texttt{| Continuum Edge And Sampling-Stability Bridge | `external\_calibration\_result` | Promote discrete-continuous bridge claims only when the sample rule, norm, error bound, or counterexample policy is stated. | Attach sampli}\\

\subsubsection*{Binding Discipline}

Each queue item is represented as a delta:

\begin{verbatim}
local claim at paper time
-> attached later source/tool/receipt/theorem
-> revised representation
-> invariant boundary and remaining residue
\end{verbatim}

This preserves the sequential story while allowing later tools, crystals, and
standard formalisms to return through the proper lane.

\subsection*{Claim Delta Ledger}

This ledger applies the paper's claim-binding queues as explicit back-application
deltas. It keeps the sequential paper story intact while allowing later
receipts, standard formalisms, CAM/crystal routes, and validators to sharpen the
claim.

\noindent\texttt{| Delta | Local claim at paper time | Later evidence | Revised representation | Boundary kept |}\\
\noindent\texttt{|---|---|---|---|---|}\\
\noindent\texttt{| Symbolic Vs Physical Carrier | This paper may use carrier language for addressable symbolic transport inside the LCR/CAM system. | Standard physics carrier terminology, local verifier receipts, material/plasma/transpor}\\
\noindent\texttt{| Electron Hole Exciton Accounting | Vacancy, complement, hole, residue, and excitation language may appear as LCR addressability/residue vocabulary. | Standard electron-hole-exciton formalism, material-model rows, band-}\\
\noindent\texttt{| Continuum Sampling Bridge | This paper may bridge discrete and continuous language only as far as its sampling, projection, or boundary rule supports. | Sampling/interpolation rules, norms, error bounds, boundary condi}\\

The revised representation records the strongest claim supported by the current evidence package. Promotion into theorem or proposition language occurs only when the named evidence is attached in the manifest or workbook replay.

\subsection*{Source-Backed Evidence Summary}

Routed archive and mirror cards are treated as provenance summaries rather than
body text. They identify candidate receipts, validators, theorem registries, or
supplemental source routes. A card strengthens this paper only when its
contribution is bound to a claim lane, evidence object, and boundary.

\noindent\texttt{| Evidence card | Score | Publication contribution | Boundary |}\\
\noindent\texttt{|---|---:|---|---|}\\
\noindent\texttt{| FORMAL: Paper 22 — C-Form: MetaForge Applied Materials Gluon | 85 | **C = the material Gluon** — the applied materials Gluon that transports the morphic Gluon (Paper 21) into physical material candidates. In the lattic}\\
\noindent\texttt{| FORMAL: Paper 11 — C-Form: Theory Admission Gate Gluon | 77 | **C = the admission filter Gluon** — the trust anchor that filters external theories by Gluon mass matching. In the lattice\_forge substrate, C is realized a}\\
\noindent\texttt{| CQE-paper-14: Paper 14 - GR Boundary-Repair Curvature | 77 | This paper defines the CQECMPLX substrate meaning of curvature as a boundary-repair demand. The closed result is a transport-ledger theorem: every route has }\\
\noindent\texttt{| CQE-paper-14.50: Paper 14.50 - Boundary-Repair Curvature Claim Contract | 77 | The contract keeps the useful object clean: repair is a real substrate quantity. Physical curvature is a proposed interpretation until prov}\\
\noindent\texttt{| SUMMARY-II-Folded-Strand-Physics: Summary Paper II — Folded Strand Physics: The Gluon as Quark, Mass, Curvature, Tower, and Moonshine | 75 | This paper presents the **physics applications** of the Gluon formalism. We d}\\
\noindent\texttt{| Additional evidence cards | 24 total | The complete card inventory is maintained in the archive evidence matrix. | Cards are source-discovery aids until bound to paper-local evidence. |}\\

\subsection*{Journal Apparatus}

\subsubsection*{Article Type And Intended Venue Fit}

This manuscript is written as a formal-methods and mathematical-systems paper
inside the series *Formalizing LCR, Unifying Standard Models*. Its intended
reader is a technical reviewer who needs claim boundaries, reproducibility
routes, and cross-paper dependencies to be visible without relying on private
context.

\subsubsection*{Structured Contribution Statement}

\noindent\texttt{| Item | Statement |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| Publication ID | `FLCR-35` |}\\
\noindent\texttt{| Legacy source slot(s) | `14, 16` |}\\
\noindent\texttt{| Ribbon role | order-2 slot-4: type the boundary, repair row, or curvature-demand condition |}\\
\noindent\texttt{| Proof form | typed boundary row and next-state admissibility |}\\
\noindent\texttt{| Received state | state emitted by prior slot 13 and reopened at original slot 14 (GR Boundary Repair Curvature) |}\\
\noindent\texttt{| Produced state | formal result of original slot 16 plus the same-family lift path toward slot 26 |}\\

\subsubsection*{Claim-Evidence Table}

\noindent\texttt{| Claim | Lane | Evidence to attach | Boundary |}\\
\noindent\texttt{|---|---|---|---|}\\
\noindent\texttt{| Theorem 35.1 | `external\_calibration\_result` | Receipt, source card, validator, citation, or CAM route named in the paper manifest | discrete repair-curvature and continuum-edge rows can be translated into GR-facing cl}\\
\noindent\texttt{| Proposition 35.2 | `normal\_form\_result` | Receipt, source card, validator, citation, or CAM route named in the paper manifest | GR-continuum translation can be imported by later papers only through its declared source,}\\
\noindent\texttt{| Protocol 35.3 | `falsifier\_or\_open\_obligation` | Receipt, source card, validator, citation, or CAM route named in the paper manifest | Einstein-field-equation identity and measured spacetime curvature remain external c}\\

\subsubsection*{Figure Plan}

\noindent\texttt{| Figure | Purpose | Caption |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| FLCR-35-F1 | Typed boundary/admission diagram | Schematic showing how `FLCR-35` turns its received state into the produced state while preserving claim lanes and residue boundaries. |}\\
\noindent\texttt{| FLCR-35-F2 | Evidence routing map | Diagram of source papers, archive cards, CAM/crystal routes, validators, and workbook replay paths used by this manuscript. |}\\
\noindent\texttt{| FLCR-35-F3 | Same-family lift context | Diagram placing this paper in the original `00-79` ribbon family and showing predecessor/successor slots. |}\\

\subsubsection*{In-Text Figure FLCR-35-F1: Typed boundary/admission diagram}

\begin{verbatim}
received state
  -> Typed boundary/admission diagram
  -> formal claim lane
  -> evidence object / receipt / citation
  -> produced state
  -> remaining residue
\end{verbatim}

\subsubsection*{Table Plan}

\noindent\texttt{| Table | Purpose |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| FLCR-35-T1 | Boundary verdict table |}\\
\noindent\texttt{| FLCR-35-T2 | Claim-lane/evidence-boundary table |}\\
\noindent\texttt{| FLCR-35-T3 | Archive evidence card and source-backed upgrade table |}\\
\noindent\texttt{| FLCR-35-T4 | Workbook replay and falsifier table |}\\

\subsubsection*{Worked Example}

Classify a candidate as admitted, repaired, boundary, rejected, or calibration-required. The example must name the input object, the operation,
the evidence object, the allowed revised claim, and the remaining boundary.

\subsubsection*{Nomenclature And Glossary}

\noindent\texttt{| Term | Paper-local meaning |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| CAM | Defined by this paper as part of the `boundary\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| admission | Defined by this paper as part of the `boundary\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| boundary | Defined by this paper as part of the `boundary\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| claim lane | Defined by this paper as part of the `boundary\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| crystal | Defined by this paper as part of the `boundary\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| falsifier | Defined by this paper as part of the `boundary\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| receipt | Defined by this paper as part of the `boundary\_action` proof role; final definition is recorded in the paper-local glossary. |}\\
\noindent\texttt{| repair row | Defined by this paper as part of the `boundary\_action` proof role; final definition is recorded in the paper-local glossary. |}\\

\subsubsection*{Appendix FLCR-35-A: Evidence Package}

The appendix records:

1. Legacy source excerpts or source-card references used in the final claim ledger.
2. Receipt and verifier paths, including pass/fail/partial status.
3. CAM/crystal query or projection rows used by the paper, with source identity and boundary.
4. Standards-window and NSIT evidence used for conformance or routing.
5. Falsifier, calibration, or external-data rows that remain unresolved.

\subsubsection*{Data And Code Availability}

The publication package contains the canonical Markdown sources, manifests, source-routing matrices, validation reports, and generated PDF/TeX outputs.

Code and verifier references are cited through manifests, archive evidence cards, receipt catalogs, or workbook replay tables. External datasets or
standards citations must be attached before any calibration-bound claim is
promoted.

\subsubsection*{Reviewer Checklist}

\noindent\texttt{| Check | Reviewer question |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| Claim lane | Does every strong claim declare its lane and evidence type? |}\\
\noindent\texttt{| Boundary | Does the paper preserve what it does not prove? |}\\
\noindent\texttt{| Reproducibility | Is there a receipt, verifier, source card, citation, or replay table for the claim? |}\\
\noindent\texttt{| Cross-paper import | Does the paper cite the prior FLCR/OPR slot before consuming its result? |}\\
\noindent\texttt{| Interpretation | Does the analog layer preserve the addressed state while changing labels/access paths? |}\\

\subsubsection*{Declarations}

No human-subjects, clinical, or animal-research protocol is asserted by this
paper. External empirical claims require separate dataset, calibration, or
domain-validation attachments. Competing-interest and funding statements are recorded in the submission metadata.

\subsection*{11. Publication Integration Addendum}

\subsubsection*{11.1 Role In The Series}

`FLCR-35` (`GR, Curvature, And Continuum Translation`) occupies the `boundary\_action` role at lift depth `1`.
The paper receives state emitted by prior slot 13 and reopened at original slot 14 (GR Boundary Repair Curvature). It produces formal result of original slot 16 plus the same-family lift path toward slot 26. The state transition is:
type the boundary condition that decides whether the state repairs, reflects, curves, or routes onward; bind state changes into causal, observer, synchronization, or obligation ledgers.

The paper-local proof form is:

\begin{verbatim}
typed boundary row and next-state admissibility
\end{verbatim}

The integration result is a typed boundary/admission table for legal next-state repair. This addendum records how that result is
consumed by the publication series without relying on editorial instructions or
private working context.

\subsubsection*{11.2 Formal Carrier}

\noindent\texttt{| Formal carrier | Function |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| boundary value problems | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| typed interfaces and admissibility conditions | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| topological boundary/interior distinction | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| falsifier rows for failed promotions | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| directed graphs and partial orders | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| causal/event ledgers | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| synchronization protocols | Formal carrier for the paper-local result. |}\\
\noindent\texttt{| traceability and provenance invariants | Formal carrier for the paper-local result. |}\\

The LCR, CAM, crystal, forge, and analog vocabulary functions as a typed access
layer over these carriers. A relabeling is admissible only when the addressed
object, evidence lane, boundary, and downstream import rule remain attached.

\subsubsection*{11.3 Claim Ledger}

\noindent\texttt{| Claim | Lane | Statement |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| Theorem 35.1 | `external\_calibration\_result` | discrete repair-curvature and continuum-edge rows can be translated into GR-facing claims only when metric, limit, and calibration assumptions are explicit |}\\
\noindent\texttt{| Proposition 35.2 | `normal\_form\_result` | GR-continuum translation can be imported by later papers only through its declared source, receipt, and lane. |}\\
\noindent\texttt{| Protocol 35.3 | `falsifier\_or\_open\_obligation` | Einstein-field-equation identity and measured spacetime curvature remain external calibration |}\\

These claims are consumed at their stated lane. A stronger downstream statement
creates a new claim envelope with its own evidence object.

\subsubsection*{11.4 Evidence Package}

\noindent\texttt{| Evidence class | Routed items | Status |}\\
\noindent\texttt{|---|---|---|}\\
\noindent\texttt{| Legacy sources | `14\_GR\_Boundary\_Repair\_Curvature.md`, `16\_Continuum\_Edge\_Residuals.md`, `supplements/SM\_BRIDGE\_SUPPLEMENT.md` | routed evidence |}\\
\noindent\texttt{| Evidence inputs | `CAM\_CLAIM\_100\_SCORE\_AUDIT.md`, `NSIT\_TOOL\_CLOSURE\_MATRIX.md`, `NSIT\_REASONED\_CLOSURE\_PASS.md`, `PAPER\_REWORKS\_CRYSTAL\_PROJECTION.json` | routed evidence |}\\
\noindent\texttt{| CAM/crystal sources | `PAPER\_REWORKS\_CRYSTAL\_PROJECTION.json`, `AGENT\_CRYSTAL\_WORK\_HARVEST.json`, `runtime standards artifact`, `notebook-derived source bundle` | routed evidence |}\\
\noindent\texttt{| Standards-window inputs | `window\_summary.json`, `node DBs`, `window DBs` | routed evidence |}\\
\noindent\texttt{| Receipts | external requirement | not attached in this source package |}\\
\noindent\texttt{| Validators | external requirement | not attached in this source package |}\\

Standards-window, runtime, and notebook-derived artifacts are treated
as evidence-routing surfaces. They support source discovery, conformance
checking, and reapplication, but they do not replace citations, receipts,
normal-form derivations, calibration rows, or falsifiers.

\subsubsection*{11.5 Results Representation}

The paper's results section is organized around five publication objects:

1. the exact object acted on at this slot;
2. the admissible operation or transformation;
3. the receipt, enumeration, derivation, lookup, or external theorem supporting
   the operation;
4. the residue or boundary left after the result;
5. the downstream import rule.

\subsubsection*{11.6 Figures And Tables}

\noindent\texttt{| Figure | Role |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| FLCR-35-F1: Typed boundary/admission diagram | Visualizes the proof object, routing, or boundary. |}\\
\noindent\texttt{| FLCR-35-F2: Evidence routing map | Visualizes the proof object, routing, or boundary. |}\\
\noindent\texttt{| FLCR-35-F3: Same-family lift context | Visualizes the proof object, routing, or boundary. |}\\

\noindent\texttt{| Table | Role |}\\
\noindent\texttt{|---|---|}\\
\noindent\texttt{| FLCR-35-T1: Boundary verdict table | Records claim lanes, evidence, sources, or falsifiers. |}\\
\noindent\texttt{| FLCR-35-T2: Claim-lane/evidence-boundary table | Records claim lanes, evidence, sources, or falsifiers. |}\\
\noindent\texttt{| FLCR-35-T3: Archive evidence card and source-backed upgrade table | Records claim lanes, evidence, sources, or falsifiers. |}\\
\noindent\texttt{| FLCR-35-T4: Workbook replay and falsifier table | Records claim lanes, evidence, sources, or falsifiers. |}\\

\subsubsection*{11.7 Limits And Falsifiers}

The paper proves only the object and domain declared in its claim ledger.
Physical, Standard Model, observer, calibration, or synthesis claims require
the additional lane evidence stated by their destination papers. CAM/crystal
and forge language is operational only when represented as an address, lookup,
receipt, validator, or reapplication path.
\end{document}
